---
title: "GO enrichment analyese of comparision to FVB"
author: "Xin Wang"
date: "2023-05-16"
output: html_document
---

 1. Summary
 2. Read the DEGs comparing to FVB
 3. Investigate the GO enrichments of DEGs
 4. Generate the interesting GO pathways dotplots
 5. Select several GO pathways for deep investigation
 6. Transcript factor analysis
   
  

# 1. Summary

This report includes quality check for sequencing data, reads mapping quality, and PCA analyses. The results of differential expression analysis  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      cache.lazy = FALSE)
```
# 2. Similary among samples

```{r libraries, cache=FALSE, warning=FALSE, error=FALSE, message=FALSE,}

library(statmod)
library(sva)

library(ggfortify)
library(ggplot2)
library(ggnewscale)
library(ggrepel)
library(edgeR)
library(clusterProfiler)
library(org.Mm.eg.db)


library(enrichplot)
library(tidyverse)

library('biomaRt')
library(factoextra)
library(DESeq2)
library(gridExtra)
library(edgeR)

library(pheatmap)

library(OmnipathR)

library(decoupleR)
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(pheatmap)
library(ggrepel)
```

# ####################################################################
# Section 1: Environment setting, reading files and PCA analyese
# ###################################################################

```{r}
setwd("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/SpecialOverlappingComparison/")
# directory for PCA
# please name the directory pathway
InDir <- c("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/SpecialOverlappingComparison/")
# set up the directory path:
DirectoryPath <- c("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/SpecialOverlappingComparison/") 

# create a directory for Transcript factors
TFDir <- ("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/SpecialOverlappingComparison/TF/")

dir.create(TFDir)

```


```{r}
#### without combination, only the first experiment
### read the normalized datasets
mydataR<-read.table(paste0(InDir,"Upk1b_CombinedSamples_ReadCounts_normalized.txt"), header=T,row.names = 1,na.strings = F, sep = "\t")

#mydataR<-read.table("../../ReadCounts/Urothelium_Combined_ProteinCoding_Annotated_uniq.txt", header=T,row.names = 1,na.strings = F, sep = "\t")
#mydataR<-read.table("../ReadCounts/Urothelium_Combined_Annotated.txt", header=T,row.names = 1,na.strings = F, sep = "\t")
head(mydataR)

# read the up-regulated genes

# FVB infection vs FVB baseline
FVBInfectUpregulated <- read.csv("Upk1b_FVB_InfectvsFVB_Baseline_UpRegulatedGenes.csv", header = T, row.names = 1)

head(FVBInfectUpregulated)
# Upk1b infection vs FVB baseline
Upk1bInfectUpregulated <- read.csv("Upk1b_UPK1B_InfectionvsFVB_Baseline_UpRegulatedGenes.csv", header = T, row.names = 1)
nrow(Upk1bInfectUpregulated)

# UPK1B_Baseline vs FVB baseline
Upk1bBaselineUpregulated <- read.csv("Upk1b_UPK1B_BaselinevsFVB_Baseline_UpRegulatedGenes.csv", header = T, row.names = 1)
nrow(Upk1bBaselineUpregulated)

# Upk1b infection vs FVB infection
UpkinfectvsWTinfectUpregulated <- read.csv("Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes.csv", header = T, row.names = 1)
nrow(UpkinfectvsWTinfectUpregulated)


# read all the DEGs
# read the up-regulated genes

# FVB infection vs FVB baseline
FVBInfectDEGs <- read.csv("Upk1b_FVB_InfectvsFVB_Baseline.DifferentialRegulatedGenes_Pvalue.csv", header = T, row.names = 1)

head(FVBInfectDEGs)
# Upk1b infection vs FVB baseline
Upk1bInfectDEGs <- read.csv("Upk1b_UPK1B_InfectionvsFVB_Baseline.DifferentialRegulatedGenes_Pvalue.csv", header = T, row.names = 1)
nrow(Upk1bInfectDEGs)

# UPK1B_Baseline vs FVB baseline
Upk1bBaselineDEGs <- read.csv("Upk1b_UPK1B_BaselinevsFVB_Baseline.DifferentialRegulatedGenes_Pvalue.csv", header = T, row.names = 1)
nrow(Upk1bBaselineDEGs)

# Upk1b infection vs FVB infection
UpkinfectvsWTinfectDEGs <- read.csv("Upk1b_UPK1B_InfectionvsFVB_Infection.DifferentialRegulatedGenes_Pvalue.csv", header = T, row.names = 1)
nrow(UpkinfectvsWTinfectDEGs)



# make a list that store the upregulate gene

UpregulatedGenevsBaseline <- list()

UpregulatedGenevsBaseline[["WTinfection"]] <- FVBInfectUpregulated$Row.names
UpregulatedGenevsBaseline[["Upk1bInfection"]] <- Upk1bInfectUpregulated$Row.names
UpregulatedGenevsBaseline[["Upk1bBaseline"]] <- Upk1bBaselineUpregulated$Row.names

#FVBInfectUpregulated$Row.names
length(UpregulatedGenevsBaseline)

# make a list that store the upregulate gene

DEGsvsBaseline <- list()

DEGsvsBaseline[["WTinfection"]] <- FVBInfectUpregulated$Row.names
DEGsvsBaseline[["Upk1bInfection"]] <- Upk1bInfectDEGs$Row.names
DEGsvsBaseline[["Upk1bBaseline"]] <- Upk1bBaselineDEGs$Row.names


```


# Comparing the gene list
```{r}
 UpGOCondtionPlot <- compareCluster(geneClusters = UpregulatedGenevsBaseline, fun = "enrichGO", OrgDb = "org.Mm.eg.db",ont="BP",keyType = 'SYMBOL', pvalueCutoff=1)
 
 write.csv(UpGOCondtionPlot, file= "UpGOCondtionPlot.csv")

# generate the top 20 pathway dotplot
pdf(file="UpGOCondtionPlot_top20.pdf", width=14, height=40)
  
  UpGOCondtionPlot_topDotPlot<- dotplot(UpGOCondtionPlot,showCategory = 20, font.size = 12,label_format = 80)
  print(UpGOCondtionPlot_topDotPlot)
  dev.off()
  
  

# select the pathway that we are interested in and generate the dotplot for these pathways
# Innate immune response: 
InnativePathway<- c(
"activation of innate immune response", "neutrophil activation", "neutrophil migration","neutrophil degranulation","cytosolic pattern recognition receptor signaling pathway","granulocyte chemotaxis", "type II interferon production", "tumor necrosis factor production", "I-kappaB kinase/NF-kappaB signaling", "phagocytosis","phagocytosis, engulfment", "regulation of inflammatory response", "integrin-mediated signaling pathway", "interleukin-2 production", "interleukin-1 production" ,"type I interferon production","cell surface toll-like receptor signaling pathway","toll-like receptor signaling pathway","stimulatory C-type lectin receptor signaling pathway","chemokine-mediated signaling pathway","cytokine-mediated signaling pathway","defense response to bacterium"
)

InnativeUpgeneGOenrichDotPlot <-
  dotplot(
    UpGOCondtionPlot,
    font.size = 12,
    label_format = 80,
    showCategory = InnativePathway
  ) +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
? dotplot
#low = "LightBlue", midpoint=0, mid="white", high = "FireBrick",
ggsave(
  "InnativeUpgeneGOenrichDotPlot.pdf",
  plot = InnativeUpgeneGOenrichDotPlot,
  height = 8,
  width = 8
)

UpGOCondtionPlot %>% as.data.frame() %>% head()
# select the genes 
CandidateGenesRegulationPathways <- UpGOCondtionPlot %>% as.data.frame() %>% filter(Cluster == "WTinfection" & Description %in% "activation of innate immune response") %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

RegulationDEGExpMatrix <- mydataR[CandidateGenesRegulationPathways,]
RegulationDEGExpMatrix
# generate the heatmap for the interesting pathway
RegulationExpMatrixHeatmap <- RegulationDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = F,show_rownames = T,treeheight_row =0, scale= "row",angle_col = "45")
RegulationExpMatrixHeatmap

ggsave(filename = "InnativeImmuneRespone_Gene.pdf", plot = RegulationExpMatrixHeatmap, height = 7, width = 5)

# Adaptive immune response
AdaptivePathway<- c(
"regulation of adaptive immune response", "antigen receptor-mediated signaling pathway", "T cell differentiation", "T cell proliferation", "T-helper 1 type immune response", "B cell activation", "T cell activation involved in immune response", "defense response to bacterium", "T-helper 17 cell differentiation", "natural killer cell activation"
)

AdaptivePathwayGOenrichDotPlot <-
  dotplot(
    UpGOCondtionPlot,
    font.size = 12,
    label_format = 80,
    showCategory = AdaptivePathway
  ) +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
? dotplot
#low = "LightBlue", midpoint=0, mid="white", high = "FireBrick",
ggsave(
  "AdaptivePathwayGOenrichDotPlot.pdf",
  plot = AdaptivePathwayGOenrichDotPlot,
  height = 8,
  width = 8
)


```


# generate heatmap for interesting pathways 
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Radiation have influence on the some specific pathway

InnativeImmPathwayDir <- paste0(DirectoryPath,"InnativeImmPathway/")

dir.create(InnativeImmPathwayDir)
setwd(InnativeImmPathwayDir)

#ARegulationPathways<- UpGOCondtionPlot %>% as.data.frame() %>% pull(Description) %>% unique()
 ## use new way of specifying visualization options
# extract the genes involved in the pathways


for (i in InnativePathway) {
  
  #i=c("cytokine-mediated signaling pathway")
  UpGOCondtionPlot %>% as.data.frame() %>% head()
  CandidateGenesRegulationPathways <- UpGOCondtionPlot %>% as.data.frame() %>% filter(Description %in% i) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

RegulationDEGExpMatrix <- mydataR[CandidateGenesRegulationPathways,]

# generate the heatmap for the interesting pathway
RegulationExpMatrixHeatmap <- RegulationDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")

replacestring <- c(" " = "_","/"="-")

CandidatePathway <- str_replace_all(i, replacestring)

ggsave(filename = (paste0(CandidatePathway,"RegulationExpMatrixHeatmap.pdf")), plot = RegulationExpMatrixHeatmap, height = 12, width = 8)

}

CandidatePathogeneRecognitionlist<-c("Tlr1","Tlr2","Tlr3","Tlr4","Tlr5","Tlr6","Tlr7","Tlr8","Tlr9","Tlr12","Tlr13","Nod1","Nod2","Ifih1","Dhx58","Clec4n","Gfer","Pparg")
CandidatePathogeneRecognitionExpMatrix <- mydataR[CandidatePathogeneRecognitionlist,]
CandidatePathogeneRecognitionExpMatrix
# generate the heatmap for the interesting pathway
CandidatePathogeneRecognitionExpMatrixHeatmap <- CandidatePathogeneRecognitionExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = F,show_rownames = T,scale= "row",angle_col = "45")
CandidatePathogeneRecognitionExpMatrixHeatmap
ggsave(filename = "PathogeneRecognitionExpMatrixHeatmap.pdf", plot = CandidatePathogeneRecognitionExpMatrixHeatmap, height = 12, width = 8)

```

```{r}
# chemokine
# https://www.rndsystems.com/resources/technical-information/chemokine-nomenclature

Chemokinelist <- c("Ccl2","Ccl3","Ccl4","Ccl5","Ccl6","Ccl7","Ccl8","Ccl9","Ccl11","Ccl12","Ccl17","Ccl20","Ccl21a","Ccl24","Ccl25","Ccl27a","Ccl28","Cxcl1","Cxcl2","Cxcl3","Pf4","Ppbp","Cxcl9","Cxcl10","Cxcl12","Cxcl13","Cxcl14","Cxcl16")
ChemokinelistExpMatrix <- mydataR[Chemokinelist,]

ChemokinelistExpMatrix 
# generate the heatmap for the interesting pathway
ChemokinelistExpMatrixHeatmap <- ChemokinelistExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = F,show_rownames = T,scale= "row",angle_col = "45")
ChemokinelistExpMatrixHeatmap
ggsave(filename = "ChemokinelistExpMatrixHeatmap.pdf", plot = ChemokinelistExpMatrixHeatmap, height = 12, width = 8)
# Cytokine
# https://cytokinesociety.org/mouse-cytokines/
Cytokinelist <- c("Il1a","Il1b","Tnf")
CytokinelistExpMatrix <- mydataR[Cytokinelist,]
# generate the heatmap for the interesting pathway
CytokinelistExpMatrixHeatmap <- CytokinelistExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = F,show_rownames = T,scale= "row",angle_col = "45")
CytokinelistlistExpMatrixHeatmap
ggsave(filename = "CytokinelistExpMatrixHeatmap.pdf", plot = CytokinelistExpMatrixHeatmap, height = 12, width = 8)

# combined 
CytokineChemokinelist <- c("Ccl2","Ccl3","Ccl4","Ccl5","Ccl6","Ccl7","Ccl8","Ccl9","Ccl20","Cxcl1","Cxcl2","Cxcl3","Cxcl9","Cxcl10","Cxcl12","Cxcl13","Il1a","Il1b","Tnf")
CytokineChemokinelistExpMatrix <- mydataR[CytokineChemokinelist,]

CytokineChemokinelistExpMatrix
CytokineChemokinelistExpMatrixHeatmap <- CytokineChemokinelistExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "CytokineChemokinelistExpMatrixHeatmap.pdf", plot = CytokineChemokinelistExpMatrixHeatmap, height = 5, width = 5)


```


# # #################################################################################
# Section 4: Detetion of transcript factors and their activities using the decoupleR
# ################################################################################

# CollecTRI is a comprehensive resource containing a curated collection of TFs and their transcriptional targets compiled from 12 different resources. This collection provides an increased coverage of transcription factors and a superior performance in identifying perturbed TFs compared to our previous DoRothEA network and other literature based GRNs. Similar to DoRothEA, interactions are weighted by their mode of regulation (activation or inhibition).

# Activity inference with Univariate Linear Model (ULM)
```{r}
# get all the normalized read counts for kidney

# set the TF directory
setwd(TFDir)
#setwd("/Users/XXW004/Documents/Projects/BrianBecknell/lcRNAseq/Results/RNAseq/TranscripFactors/")

# The comparison FVB_InfectvsFVB:
```

# collecting the TFs and their Target Genes
```{r}
# here we collecte a comprehensive resource containing a curated collection of TFs and their transcript targets comping from 12 different resources . This collection proivides an increased coverage of transcript factors and a superior performance 
# in identitying pertubed TFs compared and other literature based GRNs.  TFs > 1,100 from 
omnipath_cache_wipe()
omnipath_set_console_loglevel('trace') # important otherwide it would give the results of human
#net <-  decoupleR::get_collectri(organism="mouse", split_complexes=FALSE)

net <-  readRDS("/Users/XXW004/Documents/Projects/RuizRosado/PIPseq/Datasets/get_collectri_human_mouse20230716/get_collectri_mouse_process_table.rds")
# use the downloaded datasets
net

PpargGenelist<- net %>% filter(source %in% c("Pparg")) 

# activated
PpargGenelist
# check the Pparg regulated gene expression
length(PpargGenelist$target)

# Draw the heatmap of PpargGene 

PparglistExpMatrix<-na.omit(mydataR[PpargGenelist$target,]) %>% as.matrix()
#CytokineChemokinelistExpMatrix
PparglistExpMatrixHeatmap <- PparglistExpMatrix %>% pheatmap(cluster_cols = F,cluster_rows  = T,show_rownames = F,scale= "row",angle_col = "45",treeheight_row=0,clustering_distance_rows="euclidean", cex=1,
      clustering_distance_cols="euclidean", clustering_method="complete")
ggsave(filename = "PparglistExpMatrixHeatmap.pdf", plot = PparglistExpMatrixHeatmap, height = 5, width = 5)

#CytokineChemokinelistExpMatrix
PparglistExpMatrixHeatmapRow <- PparglistExpMatrix %>% pheatmap(cluster_cols = F,cluster_rows  = T,show_rownames = T,scale= "row",angle_col = "45",treeheight_row=0,clustering_distance_rows="euclidean", cex=1,
      clustering_distance_cols="euclidean", clustering_method="complete")
ggsave(filename = "PparglistExpMatrixHeatmapRow.pdf", plot = PparglistExpMatrixHeatmapRow, height = 40, width = 5)
# reference: https://www.biostars.org/p/287512/
# check the cluster gene order 
#PparglistRepExpMatrixHeatmap$tree_row[["order"]],]
clusters<-rownames(PparglistExpMatrix[PparglistExpMatrixHeatmap$tree_row[["order"]],])

FinalPpargExpressionOrdered<- PparglistExpMatrix[PparglistExpMatrixHeatmap$tree_row[["order"]],]

write.csv(FinalPpargExpressionOrdered, "FinalPpargExpressionOrdered.csv")
clusters <- sort(cutree(PparglistExpMatrixHeatmap$tree_row,k=8))
cutree(PparglistExpMatrixHeatmap$tree_row,k=8)
PparglistExpMatrixHeatmap$tree_row
#clusters <- rownames(subsetDat[heat$tree_row[["order"]],])

PpargGenelistRep<- net %>% filter(source %in% c("Pparg")) %>% filter(mor == -1)
PparglistRepExpMatrix<-mydataR[PpargGenelistRep$target,]
#CytokineChemokinelistExpMatrix
PparglistRepExpMatrixHeatmap <- na.omit(PparglistRepExpMatrix) %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = T,show_rownames = T,scale= "row",angle_col = "45",treeheight_row=0)
ggsave(filename = "PparglistRepExpMatrixHeatmap.pdf", plot = PparglistRepExpMatrixHeatmap, height = 5, width = 5)


?pheatmap
PpargGenelistRAct<- net %>% filter(source %in% c("Pparg")) %>% filter(mor == 1)
PpargGenelistRActExpMatrix<-mydataR[PpargGenelistRAct$target,]
#CytokineChemokinelistExpMatrix
PpargGenelistRActExpMatrixHeatmap <- na.omit(PpargGenelistRActExpMatrix) %>% as.matrix() %>% pheatmap(cluster_cols = F,cluster_rows  = T,show_rownames = T,scale= "row",angle_col = "45",treeheight_row=0)
ggsave(filename = "PpargGenelistRActExpMatrixHeatmap.pdf", plot = PpargGenelistRActExpMatrixHeatmap, height = 5, width = 5)

```



```{r}
# create dir

TFFVBInfection <- paste0(TFDir, "/","FVBinfection/")
dir.create(TFFVBInfection)
setwd(TFFVBInfection)

# the genesets
FVBInfectUpregulated
# 
# the expression between FVB infection and FVB
mydataR %>% head()

FVBInfectExpression<- mydataR[,1:8]
FVBInfectExpression %>% head()

```


```{r}
# get the design 

FVBInfectionDesign <- tibble(sample=colnames(FVBInfectExpression), condition=c(rep("FVB",4),rep("FVBinfection",4)))
FVBInfectionDesign
# get the t value of the DEGs between two conditions
# all the details store into FVBInfectDEGs
FVBInfectDEGs %>% head()
#res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

# extract t-value per gene
FVBInfectDEGsets <- FVBInfectDEGs %>% mutate(t = -log10(PValue) * logFC) %>% filter(Padjust <=0.05 & (logFC >=0.58 |logFC <=-0.58)) %>% dplyr::select(Row.names, t) %>% 
    filter(!is.na(t)) %>% 
    column_to_rownames(var = "Row.names") %>%
    as.matrix()
# check the DEG and t-value per genes
FVBInfectDEGsets%>% head()
```


# we ignore this due to we are not focusing on the whole gene expression but interested into the differentially expression
```{r}
# Activity inference wiht univariate linear model: To infer TF enrichment scores we run the univaribate linera model methods, for each sample in our datasets and each TF in our network, it fits a linear model that preducts the observed gene expression based solely on the TF's TF-gene interaction weights. 
# Once fitted the obtained t-value of the slope ist he score, If it is positive, we interpret that the TF is active and if it is negative we interpret that it is inactive.
FVBInfectDEGsample_acts <- run_ulm(mat=FVBInfectDEGsets, net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)
FVBInfectDEGsample_acts
#From the obtained results we will observe the most variable activities across samples in a heat-map:
#n_tfs <-40
# vsualization
# From the obtained results we will observe the most variable activities across samples in a heat-map:

FVBInfectDEGsample_acts_mat <- FVBInfectDEGsample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
FVBInfectDEGsample_acts_mat %>% head()
# Scale per feature
# Get all the tfs with more variable means across clusters
FVBInfectDEGtfs <- FVBInfectDEGsample_acts %>%
  group_by(source) %>%
  summarise(std = sd(score)) %>%
  arrange(-abs(std)) %>%
  #head(n_tfs) %>%
  pull(source)

write.csv(file = "FVBInfectDEGsets.Trancriptfactor.SampleDetails.csv", FVBInfectDEGsample_acts)


FVBInfectDEGtfs %>% length()
# overlapping with DEGs
FVBInfectDEGDEGs<- FVBInfectDEGs$Row.names
FVBInfectDEGDEGs %>% length()

FVBInfectDEGtfs_DEG_verlapping<-intersect(FVBInfectDEGtfs, FVBInfectDEGDEGs)
FVBInfectDEGtfs_DEG_verlapping

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)
# Generate the expression profiles of these overlapping genes
FVBInfectDEGtfs_DEG_verlappingHeatmap<- FVBInfectExpression[FVBInfectDEGtfs_DEG_verlapping,] %>% pheatmap(scale = "row",border_color = NA, color=my_color,angle_col = "45") 
# top transcript that show dramatical different
ggsave("FVBInfectDEGsets.tfs_DEG_verlappingHeatmap_Exp.pdf", plot =FVBInfectDEGtfs_DEG_verlappingHeatmap, height = 10, width = 6 )

FVBInfectDEGsample_acts_mat_overlaping<- FVBInfectDEGsample_acts_mat[,colnames(FVBInfectDEGsample_acts_mat) %in% FVBInfectDEGtfs_DEG_verlapping]

t(FVBInfectDEGsample_acts_mat_overlaping)
#sample_acts_mat <- scale(sample_acts_mat)


my_breaks <- c(seq(-3, 0, length.out=ceiling(palette_length/2) + 1),
               seq(0.05, 3, length.out=floor(palette_length/2)))

# Plot
FVBInfectDEGTopTFpheatmap<-pheatmap(t(FVBInfectDEGsample_acts_mat), scale = "row",border_color = NA, color=my_color, breaks = my_breaks) 
t(sample_acts_mat) %>% head()
ggsave("FVBInfectDEGsets.TopTFpheatmap_FromAllExp.pdf", plot =FVBInfectDEGTopTFpheatmap, height = 10, width = 6 )

# show the score of 
n_tfs=40
# Filter top TFs in both signs
FVBInfectDEGf_contrast_acts <- FVBInfectDEGsample_acts %>%
  mutate(rnk = NA)
msk <- FVBInfectDEGf_contrast_acts$score > 0
FVBInfectDEGf_contrast_acts[msk, 'rnk'] <- rank(-FVBInfectDEGf_contrast_acts[msk, 'score'])
FVBInfectDEGf_contrast_acts[!msk, 'rnk'] <- rank(-abs(FVBInfectDEGf_contrast_acts[!msk, 'score']))
FVBInfectDEGtfs <- FVBInfectDEGf_contrast_acts %>%
  arrange(rnk) %>%
  head(n_tfs) %>%
  pull(source)
FVBInfectDEGf_contrast_acts <- FVBInfectDEGf_contrast_acts %>%
  filter(source %in% FVBInfectDEGtfs)

# Plot
FVBInfectDEGTFRankingSoreFigure<-ggplot(FVBInfectDEGf_contrast_acts, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("TFs")

ggsave(filename = "FVBInfectDEGTFRankingSoreFigure.pdf",plot =FVBInfectDEGTFRankingSoreFigure, height = 6, width = 9 )

```

# we infer the TF from the comparisons between Up1k infection vs WT

```{r}
# create dir

TFUpk1bInfection <- paste0(TFDir, "/","Upk1binfection/")
dir.create(TFUpk1bInfection)
setwd(TFUpk1bInfection)

# 
# the expression between FVB infection and FVB
mydataR %>% head()

Upk1bInfectExpression<- mydataR[,c(1:4,9:12)]
Upk1bInfectExpression %>% head()

```


```{r}
# get the design 

Upk1bInfectionDesign <- tibble(sample=colnames(Upk1bInfectExpression), condition=c(rep("FVB",4),rep("Upk1bInfection",4)))
Upk1bInfectionDesign
# get the t value of the DEGs between two conditions
# all the details store into Upk1bInfectDEGs
Upk1bInfectDEGs %>% head()
#res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

# extract t-value per gene
Upk1bInfectDEGsets <- Upk1bInfectDEGs %>% mutate(t = -log10(PValue) * logFC) %>% filter(Padjust <=0.05 & (logFC >=0.58 |logFC <=-0.58)) %>% dplyr::select(Row.names, t) %>% 
    filter(!is.na(t)) %>% 
    column_to_rownames(var = "Row.names") %>%
    as.matrix()
# check the DEG and t-value per genes
Upk1bInfectDEGsets%>% head()
```


# we ignore this due to we are not focusing on the whole gene expression but interested into the differentially expression
```{r}
# Activity inference wiht univariate linear model: To infer TF enrichment scores we run the univaribate linera model methods, for each sample in our datasets and each TF in our network, it fits a linear model that preducts the observed gene expression based solely on the TF's TF-gene interaction weights. 
# Once fitted the obtained t-value of the slope ist he score, If it is positive, we interpret that the TF is active and if it is negative we interpret that it is inactive.
Upk1bInfectDEGsample_acts <- run_ulm(mat=Upk1bInfectDEGsets, net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)
Upk1bInfectDEGsample_acts
#From the obtained results we will observe the most variable activities across samples in a heat-map:
#n_tfs <-40
# vsualization
# From the obtained results we will observe the most variable activities across samples in a heat-map:

Upk1bInfectDEGsample_acts_mat <- Upk1bInfectDEGsample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
Upk1bInfectDEGsample_acts_mat %>% head()
# Scale per feature
# Get all the tfs with more variable means across clusters
Upk1bInfectDEGtfs <- Upk1bInfectDEGsample_acts %>%
  group_by(source) %>%
  summarise(std = sd(score)) %>%
  arrange(-abs(std)) %>%
  #head(n_tfs) %>%
  pull(source)

write.csv(file = "Upk1bInfectDEGsets.Trancriptfactor.SampleDetails.csv", Upk1bInfectDEGsample_acts)


Upk1bInfectDEGtfs %>% length()
# overlapping with DEGs
Upk1bInfectDEGDEGs<- Upk1bInfectDEGs$Row.names
Upk1bInfectDEGDEGs %>% length()

Upk1bInfectDEGtfs_DEG_verlapping<-intersect(Upk1bInfectDEGtfs, Upk1bInfectDEGDEGs)
Upk1bInfectDEGtfs_DEG_verlapping

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)
# Generate the expression profiles of these overlapping genes
Upk1bInfectDEGtfs_DEG_verlappingHeatmap<- Upk1bInfectExpression[Upk1bInfectDEGtfs_DEG_verlapping,] %>% pheatmap(scale = "row",border_color = NA, color=my_color,angle_col = "45") 
# top transcript that show dramatical different
ggsave("Upk1bInfectDEGsets.tfs_DEG_verlappingHeatmap_Exp.pdf", plot =Upk1bInfectDEGtfs_DEG_verlappingHeatmap, height = 10, width = 6 )

Upk1bInfectDEGsample_acts_mat_overlaping<- Upk1bInfectDEGsample_acts_mat[,colnames(Upk1bInfectDEGsample_acts_mat) %in% Upk1bInfectDEGtfs_DEG_verlapping]


# show the score of 
n_tfs=40
# Filter top TFs in both signs
Upk1bInfectDEGf_contrast_acts <- Upk1bInfectDEGsample_acts %>%
  mutate(rnk = NA)
msk <- Upk1bInfectDEGf_contrast_acts$score > 0
Upk1bInfectDEGf_contrast_acts[msk, 'rnk'] <- rank(-Upk1bInfectDEGf_contrast_acts[msk, 'score'])
Upk1bInfectDEGf_contrast_acts[!msk, 'rnk'] <- rank(-abs(Upk1bInfectDEGf_contrast_acts[!msk, 'score']))
Upk1bInfectDEGtfs <- Upk1bInfectDEGf_contrast_acts %>%
  arrange(rnk) %>%
  head(n_tfs) %>%
  pull(source)
Upk1bInfectDEGf_contrast_acts <- Upk1bInfectDEGf_contrast_acts %>%
  filter(source %in% Upk1bInfectDEGtfs)

# Plot
Upk1bInfectDEGTFRankingSoreFigure<-ggplot(Upk1bInfectDEGf_contrast_acts, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("TFs")

ggsave(filename = "Upk1bInfectDEGTFRankingSoreFigure.pdf",plot =Upk1bInfectDEGTFRankingSoreFigure, height = 6, width = 9 )

```



# we infer the TF from the comparisons between Up1k vs WT

```{r}
# create dir

TFUpk1bBaseline <- paste0(TFDir, "/","Upk1bBaselineion/")
dir.create(TFUpk1bBaseline)
setwd(TFUpk1bBaseline)

# the genesets
Upk1bBaselineDEGs
# 
# the expression between FVB infection and FVB
mydataR %>% head()

Upk1bBaselineExpression<- mydataR[,c(1:4,13:16)]
Upk1bBaselineExpression %>% head()

```


```{r}
# get the design 

Upk1bBaselineDesign <- tibble(sample=colnames(Upk1bBaselineExpression), condition=c(rep("FVB",4),rep("Upk1bBaseline",4)))
Upk1bBaselineDesign
# get the t value of the DEGs between two conditions
# all the details store into Upk1bBaselineDEGs
Upk1bBaselineDEGs %>% head()
#res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

# extract t-value per gene
Upk1bBaselineDEGsets <- Upk1bBaselineDEGs %>% mutate(t = -log10(PValue) * logFC) %>% filter(Padjust <=0.05 & (logFC >=0.58 |logFC <=-0.58)) %>% dplyr::select(Row.names, t) %>% 
    filter(!is.na(t)) %>% 
    column_to_rownames(var = "Row.names") %>%
    as.matrix()
# check the DEG and t-value per genes
Upk1bBaselineDEGsets%>% head()
```


# we ignore this due to we are not focusing on the whole gene expression but interested into the differentially expression
```{r}
# Activity inference wiht univariate linear model: To infer TF enrichment scores we run the univaribate linera model methods, for each sample in our datasets and each TF in our network, it fits a linear model that preducts the observed gene expression based solely on the TF's TF-gene interaction weights. 
# Once fitted the obtained t-value of the slope ist he score, If it is positive, we interpret that the TF is active and if it is negative we interpret that it is inactive.
Upk1bBaselineDEGsample_acts <- run_ulm(mat=Upk1bBaselineDEGsets, net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)
Upk1bBaselineDEGsample_acts
#From the obtained results we will observe the most variable activities across samples in a heat-map:
#n_tfs <-40
# vsualization
# From the obtained results we will observe the most variable activities across samples in a heat-map:

Upk1bBaselineDEGsample_acts_mat <- Upk1bBaselineDEGsample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
Upk1bBaselineDEGsample_acts_mat %>% head()
# Scale per feature
# Get all the tfs with more variable means across clusters
Upk1bBaselineDEGtfs <- Upk1bBaselineDEGsample_acts %>%
  group_by(source) %>%
  summarise(std = sd(score)) %>%
  arrange(-abs(std)) %>%
  #head(n_tfs) %>%
  pull(source)

write.csv(file = "Upk1bBaselineDEGsets.Trancriptfactor.SampleDetails.csv", Upk1bBaselineDEGsample_acts)


Upk1bBaselineDEGtfs %>% length()
# overlapping with DEGs
Upk1bBaselineDEGDEGs<- Upk1bBaselineDEGs$Row.names
Upk1bBaselineDEGDEGs %>% length()

Upk1bBaselineDEGtfs_DEG_verlapping<-intersect(Upk1bBaselineDEGtfs, Upk1bBaselineDEGDEGs)
Upk1bBaselineDEGtfs_DEG_verlapping

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)
# Generate the expression profiles of these overlapping genes
Upk1bBaselineDEGtfs_DEG_verlappingHeatmap<- Upk1bBaselineExpression[Upk1bBaselineDEGtfs_DEG_verlapping,] %>% pheatmap(scale = "row",border_color = NA, color=my_color,angle_col = "45") 
# top transcript that show dramatical different
ggsave("Upk1bBaselineDEGsets.tfs_DEG_verlappingHeatmap_Exp.pdf", plot =Upk1bBaselineDEGtfs_DEG_verlappingHeatmap, height = 10, width = 6 )

Upk1bBaselineDEGsample_acts_mat_overlaping<- Upk1bBaselineDEGsample_acts_mat[,colnames(Upk1bBaselineDEGsample_acts_mat) %in% Upk1bBaselineDEGtfs_DEG_verlapping]


# show the score of 
n_tfs=40
# Filter top TFs in both signs
Upk1bBaselineDEGf_contrast_acts <- Upk1bBaselineDEGsample_acts %>%
  mutate(rnk = NA)
msk <- Upk1bBaselineDEGf_contrast_acts$score > 0
Upk1bBaselineDEGf_contrast_acts[msk, 'rnk'] <- rank(-Upk1bBaselineDEGf_contrast_acts[msk, 'score'])
Upk1bBaselineDEGf_contrast_acts[!msk, 'rnk'] <- rank(-abs(Upk1bBaselineDEGf_contrast_acts[!msk, 'score']))
Upk1bBaselineDEGtfs <- Upk1bBaselineDEGf_contrast_acts %>%
  arrange(rnk) %>%
  head(n_tfs) %>%
  pull(source)
Upk1bBaselineDEGf_contrast_acts <- Upk1bBaselineDEGf_contrast_acts %>%
  filter(source %in% Upk1bBaselineDEGtfs)

# Plot
Upk1bBaselineDEGTFRankingSoreFigure<-ggplot(Upk1bBaselineDEGf_contrast_acts, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("TFs")

ggsave(filename = "Upk1bBaselineDEGTFRankingSoreFigure.pdf",plot =Upk1bBaselineDEGTFRankingSoreFigure, height = 6, width = 9 )

```


# we infer the TF from the comparisons between Up1k infection vs wt infection

```{r}
# create dir
UpkinfectvsWTinfect <- paste0(TFDir, "/","UpkinfectvsWTinfect/")
dir.create(UpkinfectvsWTinfect)
setwd(UpkinfectvsWTinfect)

# the genesets
UpkinfectvsWTinfectUpregulated
# 
# the expression between FVB infection and FVB
mydataR %>% head()

# please correct this 
UpkinfectvsWTinfectExpression<- mydataR[,c(5:8,13:16)]
UpkinfectvsWTinfectExpression %>% head()

```


```{r}
# get the design 

UpkinfectvsWTinfectionDesign <- tibble(sample=colnames(UpkinfectvsWTinfectExpression), condition=c(rep("Upk1binfection",4),rep("FVBinfection",4)))
UpkinfectvsWTinfectionDesign
# get the t value of the DEGs between two conditions
# all the details store into UpkinfectvsWTinfectDEGs
UpkinfectvsWTinfectDEGs %>% head()
#res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

# extract t-value per gene
UpkinfectvsWTinfectDEGsets <- UpkinfectvsWTinfectDEGs %>% mutate(t = -log10(PValue) * logFC) %>% filter(Padjust <=0.05 & (logFC >=0.58 |logFC <=-0.58)) %>% dplyr::select(Row.names, t) %>% 
    filter(!is.na(t)) %>% 
    column_to_rownames(var = "Row.names") %>%
    as.matrix()
# check the DEG and t-value per genes
UpkinfectvsWTinfectDEGsets%>% head()
```




# ###########################
# generate the PCA results
# ###########################



```{r}

setwd(DEGDir)
# without removing outlier
#Urothelium<-mydataR[,c(4:11)]

# remove outlier
Urothelium<-mydataR[,c(10:18,3:9)]


head(Urothelium)
### plot all the pca
### quantile normalize the dataset

Allcounts<-normalizeQuantiles(Urothelium)

#head(Allcounts)
group_all<- factor(c(rep("FVB_Baseline",4), rep("FVB_Infect",4),rep("UPK1B_Baseline",4), rep("UPK1B_Infect",4)))

y<-DGEList(counts=Allcounts, group=group_all)

#edgeR::cpm(y)
### filter low counts genes
keep<-rowSums(y$counts) > 5

# use cpm normalization
keep<-rowSums(edgeR::cpm(y)>0.5) >=2

#table(keep)
genelist.filted<-y[keep, ,keep.lib.sizes=FALSE]

##### compsosition bias 标准化， 

genelist.norm<-calcNormFactors(genelist.filted,method="TMM")
genelist.norm.log<-edgeR::cpm(genelist.norm, log=TRUE)
genelist.norm.log<-as.data.frame(genelist.norm.log)
Condition<- factor(group_all)

```

# we only need to generate once, so the following PCA analyes is not generated again.
# PCA analyses of samples
# Please ignore this section (L179 - L330)
```{r}
# generate the results from removing the batch effectss
# #genelist.norm.logremoveBatch <- ComBat(genelist.norm.log, batch = group_all)
# 
# genelist.norm.log.pcaRemoveBatch <- prcomp(t(genelist.norm.logremoveBatch), scale = TRUE)
# 
# genelist.norm.log.pcaRemoveBatch$x %>% as.data.frame () %>% 
#   ggplot(aes(x=PC1,y=PC2,color=factor(label_name))) + geom_point(size=1) + 
#   geom_text_repel(label=colnames(genelist.norm.log),segment.size=0.01,hjust=0.2, size=2)+
#   #labs(x= paste0("PC1: ", round(var_explained[1]*100,1),"%"),
#   #     y=paste0("PC2: ",round(var_explained[2]*100,1),"%")) +
#   theme_classic()
# 
# 
# head(genelist.norm.log)

# Run PCA using Prcommp()
genelist.norm.log.pca <- prcomp(t(genelist.norm.log), scale = TRUE)

#genelist.norm.log.pca
# Generate a PCA plots]
# Sdev provide the standard deviation of principal components
#paste0(str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,c(3,6)], sep="_")

#paste0(str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,3],"_",
 #      str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,6])

var_explained <- genelist.norm.log.pca$sdev^2/sum(genelist.norm.log.pca$sdev^2)
# add the

```

```{r}
#rep_str =c("_BecknellB" = "","_VC_1"="","_L001_count"="")
#colnames(genelist.norm.log)
#str_replace_all(colnames(genelist.norm.log),rep_str)
colnames(genelist.norm.log)
PCAAnalyses<-genelist.norm.log.pca$x %>% 
  as.data.frame %>%
  ggplot(aes(x=PC1,y=PC2,color=Condition)) + geom_point(size=1) + 
  geom_text_repel(label=colnames(genelist.norm.log),segment.size=0.01,hjust=0.2, size=2.5)+
  #geom_text_repel(label=str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,3],segment.size=0.01,hjust=0.2, size=2)+
  labs(x= paste0("PC1: ", round(var_explained[1]*100,1),"%"),
       y=paste0("PC2: ",round(var_explained[2]*100,1),"%")) +
  theme_classic()
#ggsave(filename = "PCAResults_TwoCondition.pdf", plot = PCAAnalyses, height = 5, width = 6)

ggsave(filename = "Upk1b_PCAResults.pdf", plot = PCAAnalyses, height = 5, width = 6)

grid.arrange(PCAAnalyses)

write.table(genelist.norm.log,file="Upk1b_CombinedSamples_ReadCounts_normalized.txt", sep="\t", quote=F)
## generate the MDS figure
label_name<-c(rep("FVB_Baseline",4), rep("FVB_Infect",4),rep("UPK1B_Baseline",4), rep("UPK1B_Infect",4))
plotMDS(genelist.norm, labels = label_name, pch = 22, bg = par("bg"),cex = 1)
colorDiff<-c(rep("blue",4), rep("red",4), rep("green",4), rep("yellow",4))
mds <- plotMDS(genelist.norm.log)
toplot <- data.frame(Dim1 = mds$x, Dim2 = mds$y, Group = group_all)
library(ggplot2)
pdf("Upk1b_MDSResults.pdf", width = 6, height = 5)
  ggplot(data=toplot, aes(x=Dim1, y=Dim2, color=Condition))+ geom_point(size=1) +
  geom_text_repel(label=colnames(genelist.norm.log),segment.size=0.1,hjust=0.2, size=2)+
  theme_classic()
dev.off()

```

# Draw barplots for the selected biomarkers
```{r}
Genemarkers <- c("Krt4", "Krt5", "Krt7","Krt8","Krt14","Krt18","Krt19","Krt20","Upk3a","Upk2","Upk1a","Upk1b", "Upk3b","Trp63", "Shh","Myocd","Actg2")
Genemarker2 <- c("Krt4", "Krt5", "Krt7","Krt8","Krt14","Krt18","Krt19","Krt20","Upk1a","Upk1b","Upk2","Upk3a", "Upk3b","Trp63", "Shh")
genelist.norm.log %>% head()
#  Extract the expression in the matrix

SelectedGenesExp<-genelist.norm.log[rownames(genelist.norm.log) %in% Genemarkers, ]

SelectedGenesExp


#str_replace_all(colnames(SelectedGenesExp), rep_str)
## update the colname 
#colnames(SelectedGenesExp) <- str_replace_all(colnames(SelectedGenesExp), rep_str)

#library("nichenetr")
library("reshape")
# Draw the heatmap

# Draw the barplot
SelectedGenesExpBarplot<-SelectedGenesExp %>% as.matrix() %>% melt() %>% 
  
  ggplot(aes(y=value, x=X1, fill=X2))+
  geom_bar(stat ="identity", position="dodge")+
  scale_fill_discrete(name="Urothelium Biomarkers",
                 # breaks=c(1, 2),
                  )+ theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
 xlab("Samples")+ 
  ylab("Normalized expression value")
SelectedGenesExpBarplot
grid.arrange(SelectedGenesExpBarplot)
ggsave(filename = "Upk1b_CombinedSamples_Urothelium_Biomarker_expression.pdf", plot = SelectedGenesExpBarplot, height = 5, width = 12)

SelectedGenesExpMatrix <- SelectedGenesExp %>% as.matrix()


# draw the heatmap of markergenes
SelectedGenesExpMatrixHeatmap <-  pheatmap(SelectedGenesExpMatrix, cluster_cols = F, cluster_rows = T,show_rownames = T,scale= "row",angle_col = "45")
SelectedGenesExpMatrixHeatmap
ggsave(filename = "Upk1b_CombinedSamples_Urothelium_Biomarker_expressionHeatmap.pdf", plot = SelectedGenesExpMatrixHeatmap, height = 5, width = 8)

```


# Draw barplots for the selected biomarkers
```{r}
DevelopmentGenemarkers <- c("Fut4","Nanog","Oct4","Isl1","Pparg","Sox17", "Foxa2", "Cxcr4","Gata4","Foxa1","Irf1","Get1","Bmp4","Shh","Ptch1","Foxf1","Gli1", "Gli3","Fzd1","Wnt7b","Wnt9b", "Wnt10a", "Wnt6", "Tbx2", "Tbx3")
#  Extract the expression in the matrix

DevelopmentGenemarkersExp <- genelist.norm.log[rownames(genelist.norm.log) %in% DevelopmentGenemarkers, ]

DevelopmentGenemarkersExp
#library("nichenetr")
library("reshape")
# Draw the heatmap

# Draw the barplot
DevelopmentGenemarkersExpBarplot<-DevelopmentGenemarkersExp %>% as.matrix() %>% melt() %>% 
  
  ggplot(aes(y=value, x=X1, fill=X2))+
  geom_bar(stat ="identity", position="dodge")+
  scale_fill_discrete(name="Urothelium deveopment Biomarkers",
                 # breaks=c(1, 2),
                  )+ theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
 xlab("Samples")+ 
  ylab("Normalized expression value") +ylim(0, 15)
DevelopmentGenemarkersExpBarplot
grid.arrange(DevelopmentGenemarkersExpBarplot)
ggsave(filename = "Upk1b_CombinedSamples_DevelopmentGenemarkersExpBarplot.pdf", plot = DevelopmentGenemarkersExpBarplot, height = 5, width = 12) 

DevelopmentGenemarkersExpMatrix <- DevelopmentGenemarkersExp %>% as.matrix()
rownames(DevelopmentGenemarkersExpMatrix)
factor(rownames(DevelopmentGenemarkersExpMatrix))


# draw the heatmap of markergenes
DevelopmentGenemarkersExpMatrixHeatmap <-  pheatmap(DevelopmentGenemarkersExpMatrix, cluster_cols = F, cluster_rows = T,show_rownames = T,scale= "row",angle_col = "45")

ggsave(filename = "Upk1b_CombinedSamples_DevelopmentGenemarkersExpMatrixHeatmap.pdf", plot = DevelopmentGenemarkersExpMatrixHeatmap, height = 5, width = 6)

```

# ############################################
# more work are needed to better focus
# generate heatmap for the urothelium cell in newborn have the ability to regulate the embronic development/ stem cell profliereation
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Urothelium have great effects on the regulation of embryonic development or other cell profliferation in neonates

RegulationPathways<- c("regulation of epithelial cell proliferation","regulation of embryonic development","regulation of neurogenesis","regulation of fibroblast proliferation","regulation of stem cell proliferation","regulation of smooth muscle cell proliferation","regulation of myeloid cell differentiation","epidermal cell differentiation","keratinocyte differentiation")
 ## use new way of specifying visualization options
color.params = list(foldChange = FCgenelist, edge = TRUE)
cex.params = list(category_label = 0.6, gene_label = 0.4)
pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_RegulationPathways_cntplot.pdf", width = 8, height = 5)

Regulationcnetplot<- cnetplot(BDEGsGO, showCategory=RegulationPathways, categorySize="pvalue", color.params =  color.params,cex.params = cex.params)
Regulationcnetplot
dev.off()

pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_RegulationPathways_heatplot.pdf", width = 15, height = 5)
Regulationheatplot<- heatplot(BDEGsGO, foldChange=FCgenelist, showCategory=RegulationPathways)
Regulationheatplot
dev.off()

pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_RegulationPathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(Regulationcnetplot, Regulationheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))

dev.off()

# generate the heatmaps

RegulationDEGs<- BDEGsGO %>% as.data.frame() %>% filter(Description %in% RegulationPathways) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

# draw the heatmap

RegulationDEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% RegulationDEGs, c(8:14)]
rownames(RegulationDEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% RegulationDEGs, 1]
colnames(RegulationDEGExpMatrix) <- str_replace_all(colnames(RegulationDEGExpMatrix), rep_str)

?pheatmap
RegulationExpMatrixHeatmap <- RegulationDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_BaselinevsFVB_Baseline_RegulationExpMatrixHeatmap.pdf", plot = DevelopmentExpMatrixHeatmap, height = 12, width = 8)

```

# generate heatmap for the urothelium cell in newborn have the ability to cell cycle phase 
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Urothelium have great effects on the regulation of embryonic development or other cell profliferation in neonates

CellCyclePathways<- c("positive regulation of cell cycle","mitotic cell cycle phase transition","regulation of cell cycle phase transition","nuclear chromosome segregation","sister chromatid segregation","nuclear division","metaphase/anaphase transition of mitotic cell cycle","mitotic spindle organization","regulation of chromosome segregation","cell cycle G1/S phase transition","cell cycle G2/M phase transition")
 ## use new way of specifying visualization options
color.params = list(foldChange = FCgenelist, edge = TRUE)
cex.params = list(category_label = 0.6, gene_label = 0.4)
pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_CellCyclePathways_cntplot.pdf", width = 11, height = 8)

CellCyclecnetplot<- cnetplot(BDEGsGO, showCategory=CellCyclePathways, categorySize="pvalue", color.params =  color.params,cex.params = cex.params ,circular=TRUE)
CellCyclecnetplot
dev.off()

?cnetplot

pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_CellCyclePathways_heatplot.pdf", width = 15, height = 5)
CellCycleheatplot<- heatplot(BDEGsGO, foldChange=FCgenelist, showCategory=CellCyclePathways)
CellCycleheatplot
dev.off()

pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_CellCyclePathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(CellCyclecnetplot, CellCycleheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))

dev.off()

# generate the heatmaps

CellCycleDEGs<- BDEGsGO %>% as.data.frame() %>% filter(Description %in% CellCyclePathways) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

# draw the heatmap

CellCyclDEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% CellCycleDEGs, c(8:14)]
rownames(CellCyclDEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% CellCycleDEGs, 1]
colnames(CellCyclDEGExpMatrix) <- str_replace_all(colnames(CellCyclDEGExpMatrix), rep_str)

?pheatmap
CellCycleExpMatrixHeatmap <- CellCyclDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_BaselinevsFVB_Baseline_CellCycleExpMatrixHeatmap.pdf", plot = CellCycleExpMatrixHeatmap, height = 9, width = 7)


pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_CellCyclePathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(CellCyclecnetplot, CellCycleheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))
dev.off()

top_row <- plot_grid(CellCyclecnetplot, CellCycleExpMatrixHeatmap)

library(ggpubr)
library(ggplot2)
library(purrr)


?heatplot

```

# generate heatmap for the urothelium cell in newborn have the ability to cell cycle phase 
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Urothelium have great effects on the regulation of embryonic development or other cell profliferation in neonates

DevelopmentPathways<- c("mesenchyme development","placenta development","epidermis development","skeletal muscle tissue development","ureteric bud development","blastocyst development","blastocyst development","smooth muscle tissue development")
 ## use new way of specifying visualization options
color.params = list(foldChange = FCgenelist, edge = TRUE)
cex.params = list(category_label = 0.6, gene_label = 0.4)
pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_DevelopmentPathways_cntplot.pdf", width = 10, height = 8)

Developmentcnetplot<- cnetplot(BDEGsGO, showCategory=DevelopmentPathways, categorySize="pvalue", color.params =  color.params,cex.params = cex.params)
Developmentcnetplot
dev.off()

pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_DevelopmentPathways_heatplot.pdf", width = 12, height = 4)
Developmentheatplot<- heatplot(BDEGsGO, foldChange=FCgenelist, showCategory=DevelopmentPathways)
Developmentheatplot
dev.off()

pdf("Upk1b_UPK1B_BaselinevsFVB_Baseline_DevelopmentPathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(Developmentcnetplot, Developmentheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))

dev.off()

# generate the heatmaps

DevelopmentDEGs<- BDEGsGO %>% as.data.frame() %>% filter(Description %in% DevelopmentPathways) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

# draw the heatmap

DevelopmentDEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% DevelopmentDEGs, c(8:14)]
rownames(DevelopmentDEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% DevelopmentDEGs, 1]
colnames(DevelopmentDEGExpMatrix) <- str_replace_all(colnames(DevelopmentDEGExpMatrix), rep_str)

?pheatmap
DevelopmentExpMatrixHeatmap <- DevelopmentDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_BaselinevsFVB_Baseline_DevelopmentExpMatrixHeatmap.pdf", plot = DevelopmentExpMatrixHeatmap, height = 12, width = 8)

```

# # #################################################################################
# Section 4: Detetion of transcript factors and their activities using the decoupleR
# ################################################################################

# CollecTRI is a comprehensive resource containing a curated collection of TFs and their transcriptional targets compiled from 12 different resources. This collection provides an increased coverage of transcription factors and a superior performance in identifying perturbed TFs compared to our previous DoRothEA network and other literature based GRNs. Similar to DoRothEA, interactions are weighted by their mode of regulation (activation or inhibition).

# Activity inference with Univariate Linear Model (ULM)
```{r}
# get all the normalized read counts for kidney

# set the TF directory
setwd(TFDir)
#setwd("/Users/XXW004/Documents/Projects/BrianBecknell/lcRNAseq/Results/RNAseq/TranscripFactors/")

# details of Urothelium expression
result_Gene_FC_normalizedlog %>% head()
UrotheliumGeneExpression<-result_Gene_FC_normalizedlog[,c(8:14)]
rownames(UrotheliumGeneExpression) <- result_Gene_FC_normalizedlog[,1]

# change the colnames

colnames(UrotheliumGeneExpression) <- str_replace_all(colnames(UrotheliumGeneExpression),rep_str)

UrotheliumGeneExpression %>% head()
# get the design 

UrotheliumDesign <- tibble(sample=str_replace_all(colnames(UrotheliumGeneExpression),rep_str), condition=c(rep("Adult",3),rep("Neonate",4)))
UrotheliumDesign
# get the t value of the DEGs between two conditions
res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

# extract t-value per gene
deg <- result_Gene_FC_normalizedlog %>% mutate(t = -log10(PValue) * logFC) %>% filter(Padjust <=0.05 & (logFC >=0.58 |logFC <=-0.58)) %>% dplyr::select(Row.names,logFC, t, PValue) %>% 
    filter(!is.na(t)) %>% 
    column_to_rownames(var = "Row.names") %>%
    as.matrix()
# check the DEG and t-value per genes
deg%>% head()
```


```{r}
# here we collecte a comprehensive resource containing a curated collection of TFs and their transcript targets comping from 12 different resources . This collection proivides an increased coverage of transcript factors and a superior performance 
# in identitying pertubed TFs compared and other literature based GRNs.  TFs > 1,100 from 
omnipath_cache_wipe()
omnipath_set_console_loglevel('trace') # important otherwide it would give the results of human
net <-  decoupleR::get_collectri(organism="mouse", split_complexes=FALSE)
net %>% head()
net %>% filter(source %in% c("Tp53"))
```


# we ignore this due to we are not focusing on the whole gene expression but interested into the differentially expression
```{r}
# Activity inference wiht univariate linear model: To infer TF enrichment scores we run the univaribate linera model methods, for each sample in our datasets and each TF in our network, it fits a linear model that preducts the observed gene expression based solely on the TF's TF-gene interaction weights. 
# Once fitted the obtained t-value of the slope ist he score, If it is positive, we interpret that the TF is active and if it is negative we interpret that it is inactive.
sample_acts <- run_ulm(mat=UrotheliumGeneExpression, net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)

#From the obtained results we will observe the most variable activities across samples in a heat-map:
#n_tfs <-40
# vsualization
# From the obtained results we will observe the most variable activities across samples in a heat-map:

sample_acts_mat <- sample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
sample_acts_mat %>% head()
# Scale per feature
# Get all the tfs with more variable means across clusters
tfs <- sample_acts %>%
  group_by(source) %>%
  summarise(std = sd(score)) %>%
  arrange(-abs(std)) %>%
  #head(n_tfs) %>%
  pull(source)

tfs %>% length()
# overlapping with DEGs
DEGs<- res$table[res$table$Padjust <=0.05 & (res$table$logFC <= -0.58|res$table$logFC >= 0.58),] %>% rownames()
DEGs %>% length()

tfs_DEG_verlapping<-intersect(tfs, DEGs)
tfs_DEG_verlapping
# Generate the expression profiles of these overlapping genes
tfs_DEG_verlappingHeatmap<- UrotheliumGeneExpression[tfs_DEG_verlapping,] %>% pheatmap(scale = "row",border_color = NA, color=my_color,angle_col = "45") 
# top transcript that show dramatical different
ggsave("tfs_DEG_verlappingHeatmap_Exp.pdf", plot =tfs_DEG_verlappingHeatmap, height = 10, width = 6 )


sample_acts_mat <- sample_acts_mat[,tfs_DEG_verlapping]
sample_acts_mat %>% t() %>% head()
# Scale per sample
#sample_acts_mat <- scale(sample_acts_mat)

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)

my_breaks <- c(seq(-3, 0, length.out=ceiling(palette_length/2) + 1),
               seq(0.05, 3, length.out=floor(palette_length/2)))

# Plot
TopTFpheatmap<-pheatmap(t(sample_acts_mat), scale = "row",border_color = NA, color=my_color, breaks = my_breaks) 
t(sample_acts_mat) %>% head()
ggsave("TopTFpheatmap_FromAllExp.pdf", plot =TopTFpheatmap, height = 10, width = 6 )

```

# we profiled the expression of target gene list
```{r}
net %>%
  filter(source == tf)
for (tf in tfs_DEG_verlapping){
  
  tf= c("Jun")
  net %>% head()
  df<- c()
  df <- net %>%
  filter(source == tf) %>%
  arrange(target) %>%
  mutate(ID = target, color = "3") %>%
  column_to_rownames('target')

inter <- sort(intersect(rownames(deg),rownames(df)))
inter
#heightlength <- round(6*length(inter))

df[inter,c('logfc', 't_value', 'Padjust')] <- deg[inter, ]
df <- df %>%
  mutate(color = if_else(mor > 0 & t_value > 0, '1', color)) %>%
  mutate(color = if_else(mor > 0 & t_value < 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value > 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value < 0, '1', color))

VolcanoPlot <- ggplot(df, aes(x = logfc, y = -log10(Padjust), color = color, size=abs(mor))) +
  geom_point() +
  scale_colour_manual(values = c("red","royalblue3","grey")) +
  geom_label_repel(aes(label = ID, size=1)) + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  ggtitle(tf)
#VolcanoPlot
ggsave(filename = paste0(tf ,"_targets_VolcanoPlot.pdf"), plot = VolcanoPlot, width = 6, height = 6)
# add a heatmap for the Rela infected genes (Regulated by Transcritptomics)
inter <- sort(intersect(rownames(deg),rownames(df)))
Pheatmap_Targets<- UrotheliumGeneExpression[inter,] %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = paste0(tf ,"_targets_peahtamap.pdf"), plot = Pheatmap_Targets, width = 6, height = 6)


}

```


# we infer pathway activatity from the the t-value of the DEGs between KO and WT
```{r}
# Run ulm
n_tfs <-40

# Run Univariate linear model (ULM) for the differentially expressed genes
contrast_acts <- run_ulm(mat=deg[, 't', drop=FALSE], net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)

contrast_acts
# Filter top TFs in both signs
## add a NA for a new column rnk
f_contrast_acts <- contrast_acts %>%
  mutate(rnk = NA)
msk <- f_contrast_acts$score >0

# we only consider those that have scores larger than 0

f_contrast_acts[msk, 'rnk'] <- rank(-f_contrast_acts[msk, 'score'])
f_contrast_acts[!msk, 'rnk'] <- rank(-abs(f_contrast_acts[!msk, 'score']))

tfs <- f_contrast_acts %>%
  arrange(rnk) %>%
  head(n_tfs) %>%
  pull(source)

tfs
f_contrast_acts <- f_contrast_acts %>%
  filter(source %in% tfs)

# generate the top transcript factor for the DEGs

# Plot
DEGTopTrasncriptFactor<- ggplot(f_contrast_acts, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("Pathways")

ggsave("UrotheliumNeonateDEGTopTrasncriptFactor.pdf",plot = DEGTopTrasncriptFactor, height = 4, width = 8)



```

```{r}
tfs
UrotheliumGeneExpression["Trp53",]
# generate the pheatmap for the top 30 TF
Pheatmap_TF <- UrotheliumGeneExpression[tfs,] %>% na.omit() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Kidney_TF_peahtamap.pdf", plot = Pheatmap_TF, width = 6, height = 6)


```

# show one specific activated pathway
```{r}
tf <- 'Rela'

# generate the pheatmap for the targets for each TF

for (tf in tfs){
  
  net %>% head()
  df<- c()
  df <- net %>%
  filter(source == tf) %>%
  arrange(target) %>%
  mutate(ID = target, color = "3") %>%
  column_to_rownames('target')

inter <- sort(intersect(rownames(deg),rownames(df)))

#heightlength <- round(6*length(inter))

df[inter,c('logfc', 't_value', 'Padjust')] <- deg[inter, ]
df <- df %>%
  mutate(color = if_else(mor > 0 & t_value > 0, '1', color)) %>%
  mutate(color = if_else(mor > 0 & t_value < 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value > 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value < 0, '1', color))

VolcanoPlot <- ggplot(df, aes(x = logfc, y = -log10(Padjust), color = color, size=abs(mor))) +
  geom_point() +
  scale_colour_manual(values = c("red","royalblue3","grey")) +
  geom_label_repel(aes(label = ID, size=1)) + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  ggtitle(tf)

ggsave(filename = paste0(tf ,"_targets_VolcanoPlot.pdf"), plot = VolcanoPlot, width = 6, height = 6)
# add a heatmap for the Rela infected genes (Regulated by Transcritptomics)
inter <- sort(intersect(rownames(deg),rownames(df)))
Pheatmap_Targets<- UrotheliumGeneExpression[inter,] %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = paste0(tf ,"_targets_peahtamap.pdf"), plot = Pheatmap_Targets, width = 6, height = 6)


}

# generate the pheatmap for the top 30 TF
Pheatmap_TF <- UrotheliumGeneExpression[tfs,] %>% na.omit() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "UrotheliumGeneExpression_TF_peahtamap.pdf", plot = Pheatmap_TF, width = 6, height = 6)

```


# For visuziation of the major signaling pathway
```{r}

# setting the progeny signaling pathway
setwd(ProgenyDir)

netProgeny <- get_progeny(organism = 'mouse', top = 500)
netProgeny

```
# Activity inference with Multivariate Linear Model (MLM)

```{r}
# Run mlm
deg
contrast_acts_Pregeny <- run_mlm(mat=deg, net=netProgeny, .source='source', .target='target',
                  .mor='weight', minsize = 5)
print(contrast_acts_Pregeny)
# Plot
ggplot(contrast_acts_Pregeny, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("Pathways")
```
# visulaization From the obtained results we will observe the obtained activities per sample in a heat-map:
```{r}
# Run mlm
UrotheliumGeneExpression
sample_acts <- run_mlm(mat=UrotheliumGeneExpression, net=netProgeny, .source='source', .target='target',
                  .mor='weight', minsize = 5)
sample_acts
# Transform to wide matrix
sample_acts_mat <- sample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
#sample_acts_mat
# Scale per feature
sample_acts_mat <- scale(sample_acts_mat)

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)

my_breaks <- c(seq(-3, 0, length.out=ceiling(palette_length/2) + 1),
               seq(0.05, 3, length.out=floor(palette_length/2)))

# Plot
pheatmap(sample_acts_mat, border_color = NA, color=my_color, breaks = my_breaks) 
```


# get all the heatmap figures for the important signaling
```{r}

# generate the pathway and targets
pathways <- contrast_acts_Pregeny %>% pull(source) %>% unique()
for (tf in pathways){


df <- netProgeny %>%
  filter(source == tf) %>%
  arrange(target) %>%
  mutate(ID = target, color = "3") %>%
  column_to_rownames('target')

inter <- sort(intersect(rownames(deg),rownames(df)))
inter

df <- df[inter, ]
df

df[,c('logfc', 't_value', 'p_value')] <- deg[inter, ]

df <- df %>%
  mutate(color = if_else(weight > 0 & t_value > 0, '1', color)) %>%
  mutate(color = if_else(weight > 0 & t_value < 0, '2', color)) %>%
  mutate(color = if_else(weight < 0 & t_value > 0, '2', color)) %>%
  mutate(color = if_else(weight < 0 & t_value < 0, '1', color))

pathwayDotplot<- ggplot(df, aes(x = weight, y = t_value, color = color)) + geom_point() +
  scale_colour_manual(values = c("red","royalblue3","grey")) +
  geom_label_repel(aes(label = ID)) + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  ggtitle(tf)
ggsave(filename = paste0(tf ,"_targets_progeney_VolcanoPlot.pdf"), plot = VolcanoPlot, width = 6, height = 6)

# generate the heatmap for the pathway
# generate the pheatmap for the top 30 TF
Pheatmap_pathway <- UrotheliumGeneExpression[inter,] %>% na.omit() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = paste0(tf ,"_targets_progeney_pheatamap.pdf"), plot = Pheatmap_pathway, width = 6, height = 6)

}

```


