---
title: "RNA-seq Analysis Report for comparison between Upk1b infection vs FVB infection"
author: "Xin Wang"
date: "2023-05-16"
output: html_document
---

 1. Summary
 2. Sequencing Quality
     2.1 Summary of sequencing quality
 3. Mapping quality
   3.1 Summary of mapping quality
 4. Expression Quantification
   4.1 Summary of reads assignment
   4.2 Expression density of samples
   4.3 Similarity between samples
 5. Differential expression
   5.1 Volcano plot
   5.2 Summary of differential analysis
   
  

# 1. Summary

This report includes quality check for sequencing data, reads mapping quality, and PCA analyses. The results of differential expression analysis  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      cache.lazy = FALSE)
```
# 2. Similary among samples

```{r libraries, cache=FALSE, warning=FALSE, error=FALSE, message=FALSE,}

# BiocManager::install("sva")
# BiocManager::install("bladderbatch")

#BiocManager::install("clusterProfiler")
#BiocManager::install("org.Mm.eg.db")
# BiocManager::install("DESeq2")
#install.packages("statmod")
#BiocManager::install("edgeR",force = TRUE)
library(statmod)
library(sva)
library(bladderbatch)
library(ggfortify)
library(ggplot2)
library(ggnewscale)
library(ggrepel)
library(edgeR)
library(clusterProfiler)
library(org.Mm.eg.db)
#keytypes(org.Mm.eg.db) 

library(enrichplot)
library(tidyverse)
### here is to get the annotation of ensemble ID
#BiocManager::install("biomaRt")
library('biomaRt')
library(factoextra)
library(DESeq2)
library(gridExtra)
library(edgeR)

library(pheatmap)
#omnipath_cache_wipe()
#remotes::install_github('saezlab/omnipathr',force = TRUE)
#remotes::install_github('saezlab/decoupleR')
#BiocManager::install("saezlab/decoupleR")
#library(OmnipathR)
#omnipath_cache_wipe()
library(OmnipathR)

library(decoupleR)
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(pheatmap)
library(ggrepel)
```

# ####################################################################
# Section 1: Environment setting, reading files and PCA analyese
# ###################################################################

```{r}
setwd("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/")
# directory for PCA
# please name the directory pathway
InDir <- c("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/RawReadCounts/")
# set up the directory path:
DirectoryPath <- c("/Users/XXW004/Documents/Projects/AshleyJackson/Upk1b_FVB/Results/") 

# create folders for DEGs, Progeny, GO, KEGG and TF analyses
# directory for DEGs
DEGDir <- paste0(DirectoryPath,"DEGs/")
# directory for Progeny
ProgenyDir <- paste0(DirectoryPath,"Progeny/")
# directory for GO enrichments
GOenrichDir <- paste0(DirectoryPath,"GOenrich/")
# directory for Transcript Factors
TFDir <-  paste0(DirectoryPath,"TranscriptFactors/")
# directory for KEGG
KEGGDir <-  paste0(DirectoryPath,"KEGG/")
# directory for CellCommunication
CellCommDir <-  paste0(DirectoryPath,"CellCommunication/")


dir.create(DEGDir, showWarnings = FALSE)
dir.create(ProgenyDir, showWarnings = FALSE)
dir.create(GOenrichDir, showWarnings = FALSE)
dir.create(TFDir, showWarnings = FALSE)
dir.create(KEGGDir, showWarnings = FALSE)
dir.create(CellCommDir, showWarnings = FALSE)
```


```{r}
#### without combination, only the first experiment
### read the data
mydataR<-read.table(paste0(InDir,"Upk1b_Combined_ProteinCoding_Ano_uniq.txt"), header=T,row.names = 1,na.strings = F, sep = "\t")

#mydataR<-read.table("../../ReadCounts/Urothelium_Combined_ProteinCoding_Annotated_uniq.txt", header=T,row.names = 1,na.strings = F, sep = "\t")
#mydataR<-read.table("../ReadCounts/Urothelium_Combined_Annotated.txt", header=T,row.names = 1,na.strings = F, sep = "\t")
head(mydataR)
```


# ###########################
# generate the PCA results
# ###########################



```{r}

setwd(DEGDir)
# without removing outlier
#Urothelium<-mydataR[,c(4:11)]

# remove outlier
Urothelium<-mydataR[,c(10:18,3:9)]


head(Urothelium)
### plot all the pca
### quantile normalize the dataset

Allcounts<-normalizeQuantiles(Urothelium)

#head(Allcounts)
group_all<- factor(c(rep("FVB_Baseline",4), rep("FVB_Infect",4),rep("UPK1B_Baseline",4), rep("UPK1B_Infect",4)))

y<-DGEList(counts=Allcounts, group=group_all)

#edgeR::cpm(y)
### filter low counts genes
keep<-rowSums(y$counts) > 5

# use cpm normalization
keep<-rowSums(edgeR::cpm(y)>0.5) >=2

#table(keep)
genelist.filted<-y[keep, ,keep.lib.sizes=FALSE]

##### compsosition bias 标准化， 

genelist.norm<-calcNormFactors(genelist.filted,method="TMM")
genelist.norm.log<-edgeR::cpm(genelist.norm, log=TRUE)
genelist.norm.log<-as.data.frame(genelist.norm.log)
Condition<- factor(group_all)

```

# we only need to generate once, so the following PCA analyes is not generated again.
# PCA analyses of samples
# Please ignore this section (L179 - L330)
```{r}
# generate the results from removing the batch effectss
# #genelist.norm.logremoveBatch <- ComBat(genelist.norm.log, batch = group_all)
# 
# genelist.norm.log.pcaRemoveBatch <- prcomp(t(genelist.norm.logremoveBatch), scale = TRUE)
# 
# genelist.norm.log.pcaRemoveBatch$x %>% as.data.frame () %>% 
#   ggplot(aes(x=PC1,y=PC2,color=factor(label_name))) + geom_point(size=1) + 
#   geom_text_repel(label=colnames(genelist.norm.log),segment.size=0.01,hjust=0.2, size=2)+
#   #labs(x= paste0("PC1: ", round(var_explained[1]*100,1),"%"),
#   #     y=paste0("PC2: ",round(var_explained[2]*100,1),"%")) +
#   theme_classic()
# 
# 
# head(genelist.norm.log)

# Run PCA using Prcommp()
genelist.norm.log.pca <- prcomp(t(genelist.norm.log), scale = TRUE)

#genelist.norm.log.pca
# Generate a PCA plots]
# Sdev provide the standard deviation of principal components
#paste0(str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,c(3,6)], sep="_")

#paste0(str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,3],"_",
 #      str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,6])

var_explained <- genelist.norm.log.pca$sdev^2/sum(genelist.norm.log.pca$sdev^2)
# add the

```

```{r}
#rep_str =c("_BecknellB" = "","_VC_1"="","_L001_count"="")
#colnames(genelist.norm.log)
#str_replace_all(colnames(genelist.norm.log),rep_str)
colnames(genelist.norm.log)
PCAAnalyses<-genelist.norm.log.pca$x %>% 
  as.data.frame %>%
  ggplot(aes(x=PC1,y=PC2,color=Condition)) + geom_point(size=1) + 
  geom_text_repel(label=colnames(genelist.norm.log),segment.size=0.01,hjust=0.2, size=2.5)+
  #geom_text_repel(label=str_split(colnames(genelist.norm.log), "_",simplify = TRUE)[,3],segment.size=0.01,hjust=0.2, size=2)+
  labs(x= paste0("PC1: ", round(var_explained[1]*100,1),"%"),
       y=paste0("PC2: ",round(var_explained[2]*100,1),"%")) +
  theme_classic()
#ggsave(filename = "PCAResults_TwoCondition.pdf", plot = PCAAnalyses, height = 5, width = 6)

ggsave(filename = "Upk1b_PCAResults.pdf", plot = PCAAnalyses, height = 5, width = 6)

grid.arrange(PCAAnalyses)

write.table(genelist.norm.log,file="Upk1b_CombinedSamples_ReadCounts_normalized.txt", sep="\t", quote=F)
## generate the MDS figure
label_name<-c(rep("FVB_Baseline",4), rep("FVB_Infect",4),rep("UPK1B_Baseline",4), rep("UPK1B_Infect",4))
plotMDS(genelist.norm, labels = label_name, pch = 22, bg = par("bg"),cex = 1)
colorDiff<-c(rep("blue",4), rep("red",4), rep("green",4), rep("yellow",4))
mds <- plotMDS(genelist.norm.log)
toplot <- data.frame(Dim1 = mds$x, Dim2 = mds$y, Group = group_all)
library(ggplot2)
pdf("Upk1b_MDSResults.pdf", width = 6, height = 5)
  ggplot(data=toplot, aes(x=Dim1, y=Dim2, color=Condition))+ geom_point(size=1) +
  geom_text_repel(label=colnames(genelist.norm.log),segment.size=0.1,hjust=0.2, size=2)+
  theme_classic()
dev.off()

```

# Draw barplots for the selected biomarkers
```{r}
Genemarkers <- c("Krt4", "Krt5", "Krt7","Krt8","Krt14","Krt18","Krt19","Krt20","Upk3a","Upk2","Upk1a","Upk1b", "Upk3b","Trp63", "Shh","Myocd","Actg2")
Genemarker2 <- c("Krt4", "Krt5", "Krt7","Krt8","Krt14","Krt18","Krt19","Krt20","Upk1a","Upk1b","Upk2","Upk3a", "Upk3b","Trp63", "Shh")
genelist.norm.log %>% head()
#  Extract the expression in the matrix

SelectedGenesExp<-genelist.norm.log[rownames(genelist.norm.log) %in% Genemarkers, ]

SelectedGenesExp


#str_replace_all(colnames(SelectedGenesExp), rep_str)
## update the colname 
#colnames(SelectedGenesExp) <- str_replace_all(colnames(SelectedGenesExp), rep_str)

#library("nichenetr")
library("reshape")
# Draw the heatmap

# Draw the barplot
SelectedGenesExpBarplot<-SelectedGenesExp %>% as.matrix() %>% melt() %>% 
  
  ggplot(aes(y=value, x=X1, fill=X2))+
  geom_bar(stat ="identity", position="dodge")+
  scale_fill_discrete(name="Urothelium Biomarkers",
                 # breaks=c(1, 2),
                  )+ theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
 xlab("Samples")+ 
  ylab("Normalized expression value")
SelectedGenesExpBarplot
grid.arrange(SelectedGenesExpBarplot)
ggsave(filename = "Upk1b_CombinedSamples_Urothelium_Biomarker_expression.pdf", plot = SelectedGenesExpBarplot, height = 5, width = 12)

SelectedGenesExpMatrix <- SelectedGenesExp %>% as.matrix()


# draw the heatmap of markergenes
SelectedGenesExpMatrixHeatmap <-  pheatmap(SelectedGenesExpMatrix, cluster_cols = F, cluster_rows = T,show_rownames = T,scale= "row",angle_col = "45")
SelectedGenesExpMatrixHeatmap
ggsave(filename = "Upk1b_CombinedSamples_Urothelium_Biomarker_expressionHeatmap.pdf", plot = SelectedGenesExpMatrixHeatmap, height = 5, width = 8)

```


# Draw barplots for the selected biomarkers
```{r}
DevelopmentGenemarkers <- c("Fut4","Nanog","Oct4","Isl1","Pparg","Sox17", "Foxa2", "Cxcr4","Gata4","Foxa1","Irf1","Get1","Bmp4","Shh","Ptch1","Foxf1","Gli1", "Gli3","Fzd1","Wnt7b","Wnt9b", "Wnt10a", "Wnt6", "Tbx2", "Tbx3")
#  Extract the expression in the matrix

DevelopmentGenemarkersExp <- genelist.norm.log[rownames(genelist.norm.log) %in% DevelopmentGenemarkers, ]

DevelopmentGenemarkersExp
#library("nichenetr")
library("reshape")
# Draw the heatmap

# Draw the barplot
DevelopmentGenemarkersExpBarplot<-DevelopmentGenemarkersExp %>% as.matrix() %>% melt() %>% 
  
  ggplot(aes(y=value, x=X1, fill=X2))+
  geom_bar(stat ="identity", position="dodge")+
  scale_fill_discrete(name="Urothelium deveopment Biomarkers",
                 # breaks=c(1, 2),
                  )+ theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
 xlab("Samples")+ 
  ylab("Normalized expression value") +ylim(0, 15)
DevelopmentGenemarkersExpBarplot
grid.arrange(DevelopmentGenemarkersExpBarplot)
ggsave(filename = "Upk1b_CombinedSamples_DevelopmentGenemarkersExpBarplot.pdf", plot = DevelopmentGenemarkersExpBarplot, height = 5, width = 12) 

DevelopmentGenemarkersExpMatrix <- DevelopmentGenemarkersExp %>% as.matrix()
rownames(DevelopmentGenemarkersExpMatrix)
factor(rownames(DevelopmentGenemarkersExpMatrix))


# draw the heatmap of markergenes
DevelopmentGenemarkersExpMatrixHeatmap <-  pheatmap(DevelopmentGenemarkersExpMatrix, cluster_cols = F, cluster_rows = T,show_rownames = T,scale= "row",angle_col = "45")

ggsave(filename = "Upk1b_CombinedSamples_DevelopmentGenemarkersExpMatrixHeatmap.pdf", plot = DevelopmentGenemarkersExpMatrixHeatmap, height = 5, width = 6)

```

# ####################################################################
# Section 2: Detections of differentially expressed genes
# ###################################################################

```{r}
#### 设计matrix ：
design <- model.matrix(~0+group_all)
colnames(design) <-levels(group_all)
design
##### 估计离散值 （Dispersion）
genelist.Disp <- estimateDisp(genelist.norm, design, robust = TRUE)

#plotBCV(genelist.Disp)

fit <- glmQLFit(genelist.Disp, design, robust=TRUE)
```

# 2.1 generate the DEGs between FVB infection vs FVB baseline
```{r}
cntrvsKD <- makeContrasts(UPK1B_Infect-FVB_Infect, levels=design)
res <- glmQLFTest(fit, contrast=cntrvsKD)
ig.edger <- res$table[p.adjust(res$table$PValue, method = "BH") < 1, ]

### add the Pajust value

res$table$Padjust<-p.adjust(res$table$PValue, method = "BH") 


### generate an datafram

results<-as.data.frame(topTags(res, n=Inf))

results %>% head()
# merge the results with the orginal expression

result_Details <- topTags(res,n=Inf)
result_Gene_FC<-merge(result_Details$table, Urothelium, by= 'row.names')
result_Gene_FC_normalizedlog<-merge(result_Details$table, genelist.norm.log, by= 'row.names')

write.csv(result_Gene_FC, file = "Upk1b_UPK1B_InfectionvsFVB_Infection.withorigin.csv")

write.csv(result_Gene_FC_normalizedlog, file = "Upk1b_UPK1B_InfectionvsFVB_Infection.withnormalized.csv")

### Adding annotation to the edgeR results
library(org.Mm.eg.db)

### gene the annotation information of the results
#ann<- AnnotationDbi::select(org.Mm.eg.db, keys=rownames(results), columns=c("ENSEMBL","SYMBOL","GENENAME"), keytype="ENSEMBL")

#ann <- select(org.Mm.eg.db, keys=rownames(res$table),columns=c("ENSEMBL","SYMBOL","GENENAME"),keytype = "ENSEMBL")
### then combine with sample expression
### generated the sample expression
Expression<-as.data.frame(res$fitted.values)

#Expression$name<-row.names(Expression)
results<-merge(results, Urothelium, by='row.names')
### print the comparision across all the samples
write.csv(results, file="Upk1b_UrotheliumExpression.AllGenes.csv")

### detect Differentially expressed genes
# up-regulated genes
BUDEG_Padjust<- res$table[res$table$Padjust <=0.05 & res$table$logFC >=0.58,]
# down-regulated genes
BDDEG_Padjust<- res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

### if we use the pvalue instead of p adjust value, we did not use P value
# BUDEG<- res$table[res$table$PValue <= 0.05 &  res$table$logFC >=0.58, ]
# BDDEG<- res$table[res$table$PValue <= 0.05  &  res$table$logFC <=-0.58, ]

nrow(BUDEG_Padjust)
nrow(BDDEG_Padjust)
## add the fold change for each gene

FCgenelist<-res$table$logFC

names(FCgenelist) <-as.character(row.names(res$table))

# sorting the FCgene list
FCgenelist <- sort(FCgenelist, decreasing = T)

# merge the upregulated genes and downregulated genes
UrotheliumExpression.UpGenes<- merge(BUDEG_Padjust, Urothelium, by= 'row.names')
UrotheliumExpression.DownGenes<- merge(BDDEG_Padjust, Urothelium, by= 'row.names')

write.csv(UrotheliumExpression.UpGenes,file="Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes.csv")
write.csv(UrotheliumExpression.DownGenes,file="Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes.csv")

UrotheliumExpression.UpGenes<- read.csv("Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes.csv")
nrow(UrotheliumExpression.UpGenes)
UrotheliumExpression.DownGenes<- read.csv("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes.csv")
nrow(UrotheliumExpression.DownGenes)
## generate the upregulated genes and down-regualted genes with normalized data
result_Gene_FC_normalizedlog<- read.csv("Upk1b_UPK1B_InfectionvsFVB_Infection.withnormalized.csv")
UrotheliumExpression_Normalized.UpGenes <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Padjust <=0.05 & result_Gene_FC_normalizedlog$logFC >= 0.58,]
nrow(UrotheliumExpression_Normalized.UpGenes)
UrotheliumExpression_Normalized.DownGenes <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Padjust <=0.05 & result_Gene_FC_normalizedlog$logFC <= -0.58,]
nrow(UrotheliumExpression_Normalized.DownGenes)

write.csv(UrotheliumExpression_Normalized.UpGenes,file="Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes_NormalizedExp.csv")
write.csv(UrotheliumExpression_Normalized.DownGenes,file="Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_NormalizedExp.csv")

BDEG<-rbind(UrotheliumExpression.UpGenes,UrotheliumExpression.DownGenes)
nrow(BDEG)

write.csv(BDEG,file="Upk1b_UPK1B_InfectionvsFVB_Infection.DifferentialRegulatedGenes_Pvalue.csv")

###  annotate the ensemble different expression with the gene ID

### draw a viocano plot to show differentially expressed genes
pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_viocanoPlot.pdf", width = 6, height = 6)

Upk1b_UPK1B_InfectionvsFVB_Infection_viocano<- ggplot(results,aes(x= results$logFC,y=-log10(results$Padjust)))+
  geom_point(size=1,color= ifelse(results$Padjust<=0.05 & results$logFC>=0.58,"red",
                                    ifelse(results$Padjust<=0.05 & results$logFC<=-0.58,"blue","gray")))+ 
  geom_text_repel(aes(label=ifelse(results$Padjust<=0.001 &(results$logFC >=2 |results$logFC <=-2) ,as.character(results$Row.names),'')),segment.size=0.01,
                  hjust=0.2, size=3)+
  
  theme_bw()+
  theme(plot.background = element_blank(),
        text = element_text(size=16),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())  + scale_x_continuous(limits=c(-6,6), breaks = c(-6, -3, 0, 3, 6))+
  xlab("log Fold Change") +ylab("-log10 adjusted P value")


grid.arrange(Upk1b_UPK1B_InfectionvsFVB_Infection_viocano)
dev.off()
results %>% arrange(Padjust,logFC) %>% head()
```

```{r}
# draw heatmap for the DEGs between Upk1b infection vs WT infetion
result_Gene_FC_normalizedlog$Row.names

result_Gene_FC_normalizedlog  %>% head()
DEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% BDEG$Row.names, c(12:15,20:23)]
rownames(DEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% BDEG$Row.names, 1]
#colnames(DEGExpMatrix) <- str_replace_all(colnames(DEGExpMatrix), rep_str)

DEGExpMatrixHeatmap <- DEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = F,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_InfectionvsFVB_Infection_DEGExpMatrixHeatmap.pdf", plot = DEGExpMatrixHeatmap, height = 5, width = 6)

?grid.arrange
```


# ####################################################################
# Section 3: functional enrichments of the DEGs
# ###################################################################
```{r}

# set the directory into GOenrich

setwd(GOenrichDir)

BDEG %>% head()
### check the enrichment of Up-regulated genes for Btret

# Here we kept all the GO enrichment values
BgoUp<-enrichGO(row.names(BUDEG_Padjust), OrgDb = "org.Mm.eg.db", ont='BP',pAdjustMethod = 'BH',pvalueCutoff = 0.05, qvalueCutoff = 0.05,keyType = 'SYMBOL')
BgoDown<-enrichGO(row.names(BDDEG_Padjust), OrgDb = "org.Mm.eg.db", ont='BP',pAdjustMethod = 'BH',pvalueCutoff = 0.05, qvalueCutoff = 0.05,keyType = 'SYMBOL')
### perform the DEGs Go enrichment
BDEGsGO<-enrichGO(BDEG$Row.names, OrgDb = "org.Mm.eg.db", ont='BP',pAdjustMethod = 'BH',pvalueCutoff = 1, qvalueCutoff = 1,keyType = 'SYMBOL')

write.csv(BgoUp, file="Upk1b_UPK1B_InfectionvsFVB_Infection.UpRegulatedGenes.GOenrich.csv")
write.csv(BgoDown, file="Upk1b_UPK1B_InfectionvsFVB_Infection.DownRegulatedGenes.GOenrich.csv")

BgoUpSimplified<-clusterProfiler::simplify(BgoUp)
BgoDownSimplified<-clusterProfiler::simplify(BgoDown)

write.csv(BgoUpSimplified, file="Upk1b_UPK1B_InfectionvsFVB_Infection.UpRegulatedGenes.GOenrichSimplified.csv")
write.csv(BgoDownSimplified, file="Upk1b_UPK1B_InfectionvsFVB_Infection.DownRegulatedGenes.GOenrichSimplified.csv")

```

# generate the figures used the simplifed GO terms

```{r}
##### generated the upregulated/downregulated GO term figures.
# for Upregulated genes
#https://bioconductor.statistik.tu-dortmund.de/packages/3.8/bioc/vignettes/ReactomePA/inst/doc/ReactomePA.html
head(as.data.frame(BgoUpSimplified))

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes_barploteGOSimplified.pdf", width = 10, height = 8)
barplot(BgoUpSimplified, showCategory = 20,font.size = 12,label_format = 80)
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes_DotplotGOSimplified.pdf", width = 10, height = 8)
dotplot(BgoUpSimplified,showCategory=20,font.size = 12,label_format = 80)
dev.off()

d <- GOSemSim::godata("org.Hs.eg.db", ont = "BP")   
compare_cluster_GO_emap_1 <- enrichplot::pairwise_termsim(BgoUpSimplified, semData = d,  method="Wang")

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_UpnRegulatedGenes_emapplotSimplified.pdf", width = 16, height = 12)
emapplot(compare_cluster_GO_emap_1)
dev.off()


head(as.data.frame(BgoDownSimplified))

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_barploteGOSimplified.pdf", width = 10, height = 8)
barplot(BgoDownSimplified, showCategory = 20,font.size = 12,label_format = 80)
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_DotplotGOSimplified.pdf", width = 10, height = 8)
dotplot(BgoDownSimplified,showCategory=20,font.size = 12,label_format = 80)
dev.off()

d <- GOSemSim::godata("org.Hs.eg.db", ont = "BP")   
compare_cluster_GO_emap_2 <- enrichplot::pairwise_termsim(BgoDownSimplified, semData = d,  method="Wang")

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_emapplotSimplified.pdf", width = 16, height = 12)
emapplot(compare_cluster_GO_emap_2)
dev.off()

```


# The figure is for the GO enrichment without simplified Go terms
```{r}
##### generated the upregulated/downregulated GO term figures.
# for Upregulated genes
#https://bioconductor.statistik.tu-dortmund.de/packages/3.8/bioc/vignettes/ReactomePA/inst/doc/ReactomePA.html
head(as.data.frame(BgoUp))

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes_barploteGO.pdf", width = 10, height = 8)
barplot(BgoUp, showCategory = 20,font.size = 12,label_format = 80)
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_UpRegulatedGenes_DotplotGO.pdf", width = 10, height = 8)
dotplot(BgoUp,showCategory=20,font.size = 12,label_format = 80)
dev.off()

d <- GOSemSim::godata("org.Hs.eg.db", ont = "BP")   
compare_cluster_GO_emap_3 <- enrichplot::pairwise_termsim(BgoUp, semData = d,  method="Wang")

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_UpnRegulatedGenes_emapplot.pdf", width = 16, height = 12)
emapplot(compare_cluster_GO_emap_3)
dev.off()


head(as.data.frame(BgoDown))

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_barploteGO.pdf", width = 10, height = 8)
barplot(BgoDown, showCategory = 20,font.size = 12,label_format = 80)
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_DotplotGO.pdf", width = 10, height = 8)
dotplot(BgoDown,showCategory=20,font.size = 12,label_format = 80)
dev.off()

d <- GOSemSim::godata("org.Hs.eg.db", ont = "BP")   
compare_cluster_GO_emap_4 <- enrichplot::pairwise_termsim(BgoDown, semData = d,  method="Wang")

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DownRegulatedGenes_emapplot.pdf", width = 16, height = 12)
emapplot(compare_cluster_GO_emap_4)
dev.off()

```


# ############################################
# more work are needed to better focus
# generate heatmap for the urothelium cell in newborn have the ability to regulate the embronic development/ stem cell profliereation
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Urothelium have great effects on the regulation of embryonic development or other cell profliferation in neonates

RegulationPathways<- c("regulation of epithelial cell proliferation","regulation of embryonic development","regulation of neurogenesis","regulation of fibroblast proliferation","regulation of stem cell proliferation","regulation of smooth muscle cell proliferation","regulation of myeloid cell differentiation","epidermal cell differentiation","keratinocyte differentiation")
 ## use new way of specifying visualization options
color.params = list(foldChange = FCgenelist, edge = TRUE)
cex.params = list(category_label = 0.6, gene_label = 0.4)
pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_RegulationPathways_cntplot.pdf", width = 8, height = 5)

Regulationcnetplot<- cnetplot(BDEGsGO, showCategory=RegulationPathways, categorySize="pvalue", color.params =  color.params,cex.params = cex.params)
Regulationcnetplot
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_RegulationPathways_heatplot.pdf", width = 15, height = 5)
Regulationheatplot<- heatplot(BDEGsGO, foldChange=FCgenelist, showCategory=RegulationPathways)
Regulationheatplot
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_RegulationPathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(Regulationcnetplot, Regulationheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))

dev.off()

# generate the heatmaps

RegulationDEGs<- BDEGsGO %>% as.data.frame() %>% filter(Description %in% RegulationPathways) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

# draw the heatmap

RegulationDEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% RegulationDEGs, c(8:14)]
rownames(RegulationDEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% RegulationDEGs, 1]
colnames(RegulationDEGExpMatrix) <- str_replace_all(colnames(RegulationDEGExpMatrix), rep_str)

?pheatmap
RegulationExpMatrixHeatmap <- RegulationDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_InfectionvsFVB_Infection_RegulationExpMatrixHeatmap.pdf", plot = DevelopmentExpMatrixHeatmap, height = 12, width = 8)

```

# generate heatmap for the urothelium cell in newborn have the ability to cell cycle phase 
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Urothelium have great effects on the regulation of embryonic development or other cell profliferation in neonates

CellCyclePathways<- c("positive regulation of cell cycle","mitotic cell cycle phase transition","regulation of cell cycle phase transition","nuclear chromosome segregation","sister chromatid segregation","nuclear division","metaphase/anaphase transition of mitotic cell cycle","mitotic spindle organization","regulation of chromosome segregation","cell cycle G1/S phase transition","cell cycle G2/M phase transition")
 ## use new way of specifying visualization options
color.params = list(foldChange = FCgenelist, edge = TRUE)
cex.params = list(category_label = 0.6, gene_label = 0.4)
pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_CellCyclePathways_cntplot.pdf", width = 11, height = 8)

CellCyclecnetplot<- cnetplot(BDEGsGO, showCategory=CellCyclePathways, categorySize="pvalue", color.params =  color.params,cex.params = cex.params ,circular=TRUE)
CellCyclecnetplot
dev.off()

?cnetplot

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_CellCyclePathways_heatplot.pdf", width = 15, height = 5)
CellCycleheatplot<- heatplot(BDEGsGO, foldChange=FCgenelist, showCategory=CellCyclePathways)
CellCycleheatplot
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_CellCyclePathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(CellCyclecnetplot, CellCycleheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))

dev.off()

# generate the heatmaps

CellCycleDEGs<- BDEGsGO %>% as.data.frame() %>% filter(Description %in% CellCyclePathways) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

# draw the heatmap

CellCyclDEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% CellCycleDEGs, c(8:14)]
rownames(CellCyclDEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% CellCycleDEGs, 1]
colnames(CellCyclDEGExpMatrix) <- str_replace_all(colnames(CellCyclDEGExpMatrix), rep_str)

?pheatmap
CellCycleExpMatrixHeatmap <- CellCyclDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_InfectionvsFVB_Infection_CellCycleExpMatrixHeatmap.pdf", plot = CellCycleExpMatrixHeatmap, height = 9, width = 7)


pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_CellCyclePathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(CellCyclecnetplot, CellCycleheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))
dev.off()

top_row <- plot_grid(CellCyclecnetplot, CellCycleExpMatrixHeatmap)

library(ggpubr)
library(ggplot2)
library(purrr)


?heatplot

```

# generate heatmap for the urothelium cell in newborn have the ability to cell cycle phase 
```{r}

# select the pathway and check the genes involved in the pathways

# 1. Urothelium have great effects on the regulation of embryonic development or other cell profliferation in neonates

DevelopmentPathways<- c("mesenchyme development","placenta development","epidermis development","skeletal muscle tissue development","ureteric bud development","blastocyst development","blastocyst development","smooth muscle tissue development")
 ## use new way of specifying visualization options
color.params = list(foldChange = FCgenelist, edge = TRUE)
cex.params = list(category_label = 0.6, gene_label = 0.4)
pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DevelopmentPathways_cntplot.pdf", width = 10, height = 8)

Developmentcnetplot<- cnetplot(BDEGsGO, showCategory=DevelopmentPathways, categorySize="pvalue", color.params =  color.params,cex.params = cex.params)
Developmentcnetplot
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DevelopmentPathways_heatplot.pdf", width = 12, height = 4)
Developmentheatplot<- heatplot(BDEGsGO, foldChange=FCgenelist, showCategory=DevelopmentPathways)
Developmentheatplot
dev.off()

pdf("Upk1b_UPK1B_InfectionvsFVB_Infection_DevelopmentPathways_combined.pdf", width = 25, height = 6)

cowplot::plot_grid(Developmentcnetplot, Developmentheatplot, ncol=2, labels=LETTERS[1:2], rel_widths = c(1,2))

dev.off()

# generate the heatmaps

DevelopmentDEGs<- BDEGsGO %>% as.data.frame() %>% filter(Description %in% DevelopmentPathways) %>% pull(geneID) %>% strsplit("/") %>% unlist() %>% unique()

# draw the heatmap

DevelopmentDEGExpMatrix <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% DevelopmentDEGs, c(8:14)]
rownames(DevelopmentDEGExpMatrix) <- result_Gene_FC_normalizedlog[result_Gene_FC_normalizedlog$Row.names %in% DevelopmentDEGs, 1]
colnames(DevelopmentDEGExpMatrix) <- str_replace_all(colnames(DevelopmentDEGExpMatrix), rep_str)

?pheatmap
DevelopmentExpMatrixHeatmap <- DevelopmentDEGExpMatrix %>% as.matrix() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Upk1b_UPK1B_InfectionvsFVB_Infection_DevelopmentExpMatrixHeatmap.pdf", plot = DevelopmentExpMatrixHeatmap, height = 12, width = 8)

```

# # #################################################################################
# Section 4: Detetion of transcript factors and their activities using the decoupleR
# ################################################################################

# CollecTRI is a comprehensive resource containing a curated collection of TFs and their transcriptional targets compiled from 12 different resources. This collection provides an increased coverage of transcription factors and a superior performance in identifying perturbed TFs compared to our previous DoRothEA network and other literature based GRNs. Similar to DoRothEA, interactions are weighted by their mode of regulation (activation or inhibition).

# Activity inference with Univariate Linear Model (ULM)
```{r}
# get all the normalized read counts for kidney

# set the TF directory
setwd(TFDir)
#setwd("/Users/XXW004/Documents/Projects/BrianBecknell/lcRNAseq/Results/RNAseq/TranscripFactors/")

# details of Urothelium expression
result_Gene_FC_normalizedlog %>% head()
UrotheliumGeneExpression<-result_Gene_FC_normalizedlog[,c(8:14)]
rownames(UrotheliumGeneExpression) <- result_Gene_FC_normalizedlog[,1]

# change the colnames

colnames(UrotheliumGeneExpression) <- str_replace_all(colnames(UrotheliumGeneExpression),rep_str)

UrotheliumGeneExpression %>% head()
# get the design 

UrotheliumDesign <- tibble(sample=str_replace_all(colnames(UrotheliumGeneExpression),rep_str), condition=c(rep("Adult",3),rep("Neonate",4)))
UrotheliumDesign
# get the t value of the DEGs between two conditions
res$table[res$table$Padjust <=0.05 & res$table$logFC <= -0.58,]

# extract t-value per gene
deg <- result_Gene_FC_normalizedlog %>% mutate(t = -log10(PValue) * logFC) %>% filter(Padjust <=0.05 & (logFC >=0.58 |logFC <=-0.58)) %>% dplyr::select(Row.names,logFC, t, PValue) %>% 
    filter(!is.na(t)) %>% 
    column_to_rownames(var = "Row.names") %>%
    as.matrix()
# check the DEG and t-value per genes
deg%>% head()
```


```{r}
# here we collecte a comprehensive resource containing a curated collection of TFs and their transcript targets comping from 12 different resources . This collection proivides an increased coverage of transcript factors and a superior performance 
# in identitying pertubed TFs compared and other literature based GRNs.  TFs > 1,100 from 
omnipath_cache_wipe()
omnipath_set_console_loglevel('trace') # important otherwide it would give the results of human
net <-  decoupleR::get_collectri(organism="mouse", split_complexes=FALSE)
net %>% head()
net %>% filter(source %in% c("Tp53"))
```


# we ignore this due to we are not focusing on the whole gene expression but interested into the differentially expression
```{r}
# Activity inference wiht univariate linear model: To infer TF enrichment scores we run the univaribate linera model methods, for each sample in our datasets and each TF in our network, it fits a linear model that preducts the observed gene expression based solely on the TF's TF-gene interaction weights. 
# Once fitted the obtained t-value of the slope ist he score, If it is positive, we interpret that the TF is active and if it is negative we interpret that it is inactive.
sample_acts <- run_ulm(mat=UrotheliumGeneExpression, net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)

#From the obtained results we will observe the most variable activities across samples in a heat-map:
#n_tfs <-40
# vsualization
# From the obtained results we will observe the most variable activities across samples in a heat-map:

sample_acts_mat <- sample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
sample_acts_mat %>% head()
# Scale per feature
# Get all the tfs with more variable means across clusters
tfs <- sample_acts %>%
  group_by(source) %>%
  summarise(std = sd(score)) %>%
  arrange(-abs(std)) %>%
  #head(n_tfs) %>%
  pull(source)

tfs %>% length()
# overlapping with DEGs
DEGs<- res$table[res$table$Padjust <=0.05 & (res$table$logFC <= -0.58|res$table$logFC >= 0.58),] %>% rownames()
DEGs %>% length()

tfs_DEG_verlapping<-intersect(tfs, DEGs)
tfs_DEG_verlapping
# Generate the expression profiles of these overlapping genes
tfs_DEG_verlappingHeatmap<- UrotheliumGeneExpression[tfs_DEG_verlapping,] %>% pheatmap(scale = "row",border_color = NA, color=my_color,angle_col = "45") 
# top transcript that show dramatical different
ggsave("tfs_DEG_verlappingHeatmap_Exp.pdf", plot =tfs_DEG_verlappingHeatmap, height = 10, width = 6 )


sample_acts_mat <- sample_acts_mat[,tfs_DEG_verlapping]
sample_acts_mat %>% t() %>% head()
# Scale per sample
#sample_acts_mat <- scale(sample_acts_mat)

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)

my_breaks <- c(seq(-3, 0, length.out=ceiling(palette_length/2) + 1),
               seq(0.05, 3, length.out=floor(palette_length/2)))

# Plot
TopTFpheatmap<-pheatmap(t(sample_acts_mat), scale = "row",border_color = NA, color=my_color, breaks = my_breaks) 
t(sample_acts_mat) %>% head()
ggsave("TopTFpheatmap_FromAllExp.pdf", plot =TopTFpheatmap, height = 10, width = 6 )

```

# we profiled the expression of target gene list
```{r}
net %>%
  filter(source == tf)
for (tf in tfs_DEG_verlapping){
  
  tf= c("Jun")
  net %>% head()
  df<- c()
  df <- net %>%
  filter(source == tf) %>%
  arrange(target) %>%
  mutate(ID = target, color = "3") %>%
  column_to_rownames('target')

inter <- sort(intersect(rownames(deg),rownames(df)))
inter
#heightlength <- round(6*length(inter))

df[inter,c('logfc', 't_value', 'Padjust')] <- deg[inter, ]
df <- df %>%
  mutate(color = if_else(mor > 0 & t_value > 0, '1', color)) %>%
  mutate(color = if_else(mor > 0 & t_value < 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value > 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value < 0, '1', color))

VolcanoPlot <- ggplot(df, aes(x = logfc, y = -log10(Padjust), color = color, size=abs(mor))) +
  geom_point() +
  scale_colour_manual(values = c("red","royalblue3","grey")) +
  geom_label_repel(aes(label = ID, size=1)) + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  ggtitle(tf)
#VolcanoPlot
ggsave(filename = paste0(tf ,"_targets_VolcanoPlot.pdf"), plot = VolcanoPlot, width = 6, height = 6)
# add a heatmap for the Rela infected genes (Regulated by Transcritptomics)
inter <- sort(intersect(rownames(deg),rownames(df)))
Pheatmap_Targets<- UrotheliumGeneExpression[inter,] %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = paste0(tf ,"_targets_peahtamap.pdf"), plot = Pheatmap_Targets, width = 6, height = 6)


}

```


# we infer pathway activatity from the the t-value of the DEGs between KO and WT
```{r}
# Run ulm
n_tfs <-40

# Run Univariate linear model (ULM) for the differentially expressed genes
contrast_acts <- run_ulm(mat=deg[, 't', drop=FALSE], net=net, .source='source', .target='target',
                  .mor='mor', minsize = 5)

contrast_acts
# Filter top TFs in both signs
## add a NA for a new column rnk
f_contrast_acts <- contrast_acts %>%
  mutate(rnk = NA)
msk <- f_contrast_acts$score >0

# we only consider those that have scores larger than 0

f_contrast_acts[msk, 'rnk'] <- rank(-f_contrast_acts[msk, 'score'])
f_contrast_acts[!msk, 'rnk'] <- rank(-abs(f_contrast_acts[!msk, 'score']))

tfs <- f_contrast_acts %>%
  arrange(rnk) %>%
  head(n_tfs) %>%
  pull(source)

tfs
f_contrast_acts <- f_contrast_acts %>%
  filter(source %in% tfs)

# generate the top transcript factor for the DEGs

# Plot
DEGTopTrasncriptFactor<- ggplot(f_contrast_acts, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("Pathways")

ggsave("UrotheliumNeonateDEGTopTrasncriptFactor.pdf",plot = DEGTopTrasncriptFactor, height = 4, width = 8)



```

```{r}
tfs
UrotheliumGeneExpression["Trp53",]
# generate the pheatmap for the top 30 TF
Pheatmap_TF <- UrotheliumGeneExpression[tfs,] %>% na.omit() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "Kidney_TF_peahtamap.pdf", plot = Pheatmap_TF, width = 6, height = 6)


```

# show one specific activated pathway
```{r}
tf <- 'Rela'

# generate the pheatmap for the targets for each TF

for (tf in tfs){
  
  net %>% head()
  df<- c()
  df <- net %>%
  filter(source == tf) %>%
  arrange(target) %>%
  mutate(ID = target, color = "3") %>%
  column_to_rownames('target')

inter <- sort(intersect(rownames(deg),rownames(df)))

#heightlength <- round(6*length(inter))

df[inter,c('logfc', 't_value', 'Padjust')] <- deg[inter, ]
df <- df %>%
  mutate(color = if_else(mor > 0 & t_value > 0, '1', color)) %>%
  mutate(color = if_else(mor > 0 & t_value < 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value > 0, '2', color)) %>%
  mutate(color = if_else(mor < 0 & t_value < 0, '1', color))

VolcanoPlot <- ggplot(df, aes(x = logfc, y = -log10(Padjust), color = color, size=abs(mor))) +
  geom_point() +
  scale_colour_manual(values = c("red","royalblue3","grey")) +
  geom_label_repel(aes(label = ID, size=1)) + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  ggtitle(tf)

ggsave(filename = paste0(tf ,"_targets_VolcanoPlot.pdf"), plot = VolcanoPlot, width = 6, height = 6)
# add a heatmap for the Rela infected genes (Regulated by Transcritptomics)
inter <- sort(intersect(rownames(deg),rownames(df)))
Pheatmap_Targets<- UrotheliumGeneExpression[inter,] %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = paste0(tf ,"_targets_peahtamap.pdf"), plot = Pheatmap_Targets, width = 6, height = 6)


}

# generate the pheatmap for the top 30 TF
Pheatmap_TF <- UrotheliumGeneExpression[tfs,] %>% na.omit() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = "UrotheliumGeneExpression_TF_peahtamap.pdf", plot = Pheatmap_TF, width = 6, height = 6)

```


# For visuziation of the major signaling pathway
```{r}

# setting the progeny signaling pathway
setwd(ProgenyDir)

netProgeny <- get_progeny(organism = 'mouse', top = 500)
netProgeny

```
# Activity inference with Multivariate Linear Model (MLM)

```{r}
# Run mlm
deg
contrast_acts_Pregeny <- run_mlm(mat=deg, net=netProgeny, .source='source', .target='target',
                  .mor='weight', minsize = 5)
print(contrast_acts_Pregeny)
# Plot
ggplot(contrast_acts_Pregeny, aes(x = reorder(source, score), y = score)) + 
    geom_bar(aes(fill = score), stat = "identity") +
    scale_fill_gradient2(low = "darkblue", high = "indianred", 
        mid = "whitesmoke", midpoint = 0) + 
    theme_minimal() +
    theme(axis.title = element_text(face = "bold", size = 12),
        axis.text.x = 
            element_text(angle = 45, hjust = 1, size =10, face= "bold"),
        axis.text.y = element_text(size =10, face= "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
    xlab("Pathways")
```
# visulaization From the obtained results we will observe the obtained activities per sample in a heat-map:
```{r}
# Run mlm
UrotheliumGeneExpression
sample_acts <- run_mlm(mat=UrotheliumGeneExpression, net=netProgeny, .source='source', .target='target',
                  .mor='weight', minsize = 5)
sample_acts
# Transform to wide matrix
sample_acts_mat <- sample_acts %>%
  pivot_wider(id_cols = 'condition', names_from = 'source',
              values_from = 'score') %>%
  column_to_rownames('condition') %>%
  as.matrix()
#sample_acts_mat
# Scale per feature
sample_acts_mat <- scale(sample_acts_mat)

# Choose color palette
palette_length = 100
my_color = colorRampPalette(c("Darkblue", "white","red"))(palette_length)

my_breaks <- c(seq(-3, 0, length.out=ceiling(palette_length/2) + 1),
               seq(0.05, 3, length.out=floor(palette_length/2)))

# Plot
pheatmap(sample_acts_mat, border_color = NA, color=my_color, breaks = my_breaks) 
```


# get all the heatmap figures for the important signaling
```{r}

# generate the pathway and targets
pathways <- contrast_acts_Pregeny %>% pull(source) %>% unique()
for (tf in pathways){


df <- netProgeny %>%
  filter(source == tf) %>%
  arrange(target) %>%
  mutate(ID = target, color = "3") %>%
  column_to_rownames('target')

inter <- sort(intersect(rownames(deg),rownames(df)))
inter

df <- df[inter, ]
df

df[,c('logfc', 't_value', 'p_value')] <- deg[inter, ]

df <- df %>%
  mutate(color = if_else(weight > 0 & t_value > 0, '1', color)) %>%
  mutate(color = if_else(weight > 0 & t_value < 0, '2', color)) %>%
  mutate(color = if_else(weight < 0 & t_value > 0, '2', color)) %>%
  mutate(color = if_else(weight < 0 & t_value < 0, '1', color))

pathwayDotplot<- ggplot(df, aes(x = weight, y = t_value, color = color)) + geom_point() +
  scale_colour_manual(values = c("red","royalblue3","grey")) +
  geom_label_repel(aes(label = ID)) + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  ggtitle(tf)
ggsave(filename = paste0(tf ,"_targets_progeney_VolcanoPlot.pdf"), plot = VolcanoPlot, width = 6, height = 6)

# generate the heatmap for the pathway
# generate the pheatmap for the top 30 TF
Pheatmap_pathway <- UrotheliumGeneExpression[inter,] %>% na.omit() %>% pheatmap(cluster_cols = F,show_rownames = T,scale= "row",angle_col = "45")
ggsave(filename = paste0(tf ,"_targets_progeney_pheatamap.pdf"), plot = Pheatmap_pathway, width = 6, height = 6)

}

```


